### 2020-02-17 Article_Final/main.tex
c

% Do not modify these
\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% -- Insert any custom LaTeX packages here --

% \package{natbib} % <-- Required for the Chicago citation style
% \package{apacite} % <-- Required for the APA citation style
% If you decide to use one of the styles above, remember to change the \bibliographystyle{} at the bottom of the document too!

\usepackage{listings} % <-- Required if you want to display program source code in your paper.
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

% -- End of custom LaTeX packages --
\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
    }
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}

% Fill in your title
\title{Exploring Science Fiction \& Fantasy Q/A}

% Do not modify the author tag below, just let it be blank
\author{}

% Fill in assignment abstract
\begin{abstract}
IN this assigment we parsed a dataset, in the form of XMLs, through a Hadoop- and pig apache. We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from science fiction and Fantasy stack exchange.

\end{abstract}

% Do not modify the following two lines
\begin{document}
\include{cover}

\lstset{style=mystyle}
\begin{document}
\include{cover}

% Insert data for the hand-in's cover page
\makecoverpage{
	master_of 		 = \par{Applied Computer Science},  % Use either: Applied Computer Science | Human-Computer Interaction
	assignment_title = \par{Exploring Science Fiction and Fantasy},  % Title of your assignment
	course_code    	 = \par{Fill in},  % Course code (ex. MA110)
	course_name      = \par{Fill in},  % Course name (ex. Systems Development)
	due_date		 = \par{Fill in},  % Due date
	student_name     = \par{Fill in},  % Your name (or names, if group – separate names with ; semicolon)
	student_number   = \par{Fill in},  % Your student ID number (or numbers, if group – separate ID numbers with ; semicolon)
	group_size		 = 1, % Number of group members (used for the declaration text)
}

% Do not modify the following two lines
\flushbottom
\maketitle

% --INTRODUCTION--
\section{Introduction}

% --RELATED WORK--
\section{Related Work}
Present related work here. 
You should read \cite{Webster2002-pw} on presenting a literature review.
Both journal papers and conference papers, such as \cite{Dingsoyr2014-xt}, are great sources.

\subsection{A subsection}
This is an example of a sub-section.

% --RESEARCH METHOD--
\section{Research Method}
Present your research method and/or design here. 
In \cite{Hevner2010-yw}, the authors discuss design science research.

Sometimes, you need to use code to illustrate your technical implementations.
Using \texttt{lstlisting} can help you with that:

\begin{lstlisting}[caption=Displaying Hello World in JavaScript]
console.log("Hello World!");
\end{lstlisting}

You might also want to display a formula, equation, stats, or other types of information requiring a math "mode" in \LaTeX.

% In-line using dollar signs
$E=mc^2$

% A free-standing formula with caption
\begin{figure}[h]
\[ E = m c^2 \]
\caption{Mass-energy equivalence}
\end{figure}

% --FINDINGS/RESULTS--
\section{Findings/Results}
Present your findings/results! 
It may be in the form of a table, such as in the case of Table \ref{tab:example}.
Upload data to Github \cite{Github_undated-kr}.

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Condition} & \textbf{n} & \textbf{p} \\
\hline
A & 5 & 0.1 \\
A & 5 & 0.1 \\
\hline
\end{tabular}
\caption{Table caption}
\end{table}

% --DISCUSSION--
\section{Discussion}
A discussion of your findings, results and previous research goes here, perhaps with a reference to Figure \ref{fig:figure_label}.

\begin{figure}[!h]
\centering
\includegraphics[width=0.5\linewidth]{images/sample_image.png}
\caption{Image caption}
\label{fig:figure_label}
\end{figure}

% --CONCLUSION--
\section{Conclusion}
Briefly conclude your study, and present thoughts on implications and further work.

\begin{itemize}
	\item One idea on further work;
	\item A second idea as well;
\end{itemize}

% --REFERENCES--
\bibliography{references} % <-- This line will generate the bibliography list automatically
\bibliographystyle{IEEEtran} % <-- Change this line if you want to use a different citation style

% Do not modify this last lines
\end{document}

### 2020-02-17 Code/task1/task1a/1aReducer.py
Added basic bash-script, trying to make 1a bash work

@@ -1,0 +1,37 @@
+#!/usr/bin/python3
+import sys
+
+"""
+reducer()
+main reducer function
+Counts words in xml-files, where the bodies are defined as 
+questions (PostTypeId = 1)
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():
+    current_word = None
+    current_count = 0
+    word = None
+    
+    for line in sys.stdin:
+        line = line.strip()
+        word,count = line.split()
+
+        count = int(count)
+        if current_word ==word:
+            current_count += count
+        else:
+            if current_word:
+                print("%s %s "%(current_word, current_count))
+            current_word = word
+            current_count = count
+            
+    if current_word== word:
+        print("%s %s "% (current_word, current_count))
+
+reducer()

### 2020-02-17 Code/task1/task1a/run1a_windows.sh

@@ -1,0 +1,35 @@
+# Assumptions:
+# 1. the dataset in the cluster is located at "news"
+# 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
+
+#Simplify task change further
+tasknumb=1a
+taskname=WordCount
+
+#Simplify task change
+mapperfile=$tasknumb$taskname.py
+reducerfile="$tasknumb"reducer.py
+outfile=output$tasknumb
+
+#Automatic removal
+hadoop fs -rm -r $outfile
+
+#For Windows-compatibility
+apt-get install dos2unix
+dos2unix $mapperfile
+dos2unix $reducerfile
+
+#Main MapReduce function
+hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
+-files $mapperfile,$reducerfile \
+-mapper $mapperfile \
+-reducer $reducerfile \
+-input posts.xml \
+-output $outfile
+
+#Read file and save it locally
+hadoop fs -cat $outfile/*
+hadoop fs -copyToLocal $outfile
+
+#Automatic cleanup
+hadoop fs -rm -r $outfile

### 2020-02-17 OldExam_Code/Task2/run.sh

@@ -1,13 +1,0 @@
-
-hadoop fs -rm -r output_2c
-rm output_2c/*
-
-hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
--input Users.xml \
--output output_2c \
--mapper 2cTopMiners.py \
--reducer 2cReducer.py
-
-hadoop fs -copyToLocal output_2c
-
-hadoop fs -cat output_2c/*

### 2020-02-17 Article_Final/main.tex
dsc

@@
 \author{}
-
+\twocolumn
 % Fill in assignment abstract
 \begin{abstract}
-IN this assigment we parsed a dataset, in the form of XMLs, through a Hadoop- and pig apache.
+In this assignment we parsed a dataset, in the form of XMLs, through a Hadoop- and pig apache.
 We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from science fiction and Fantasy stack exchange.
@@
 % Do not modify the following two lines
-\begin{document}
-\include{cover}
-
 \lstset{style=mystyle}
@@
 	course_code    	 = \par{Fill in},  % Course code (ex. MA110)
-	course_name      = \par{Fill in},  % Course name (ex. Systems Development)
-	due_date		 = \par{Fill in},  % Due date
-	student_name     = \par{Fill in},  % Your name (or names, if group – separate names with ; semicolon)
-	student_number   = \par{Fill in},  % Your student ID number (or numbers, if group – separate ID numbers with ; semicolon)
-	group_size		 = 1, % Number of group members (used for the declaration text)
+	course_name      = \par{Big Data},  % Course name (ex. Systems Development)
+	due_date		 = \par{24. February},  % Due date
+	student_name     = \par{-},  % Your name (or names, if group – separate names with ; semicolon)
+	student_number   = \par{865317, 866354},  % Your student ID number (or numbers, if group – separate ID numbers with ; semicolon)
+	group_size		 = 2, % Number of group members (used for the declaration text)
 }
@@
 \section{Introduction}
+This report is of a structure where each task is independent and separately reported, frequently referring to each other due to their similarity.
+Each contains our assumptions about what the task is asking for, implementation, and any notes/reflections if necessary, opting to add notes/reflection more than necessary rather than less than necessary.\\
 
-% --RELATED WORK--
-\section{Related Work}
-Present related work here. 
-You should read \cite{Webster2002-pw} on presenting a literature review.
-Both journal papers and conference papers, such as \cite{Dingsoyr2014-xt}, are great sources.
+We chose to work together because both of us have python background, choosing python as main programming language.
+We explored a Science Fiction \& Fantasy Q\&A StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/scifi.stackexchange.com.7z} (accessed 17.02.2020) through Hadoop and Pig.\\
+Hadoop is used to store and process big data, it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs.
+Hadoop provides a framework which allow users to write and test distributed systems and does not rely on hardware to provide fault tolerance, making it less apt for our small-scale applications, yet we use it for the experience.
+Pig is a MapReduce abstraction, working on Hadoop methods, that we use in some tasks due to its efficiency.
+We have elected to use both pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both show our ability to employ both methods and get experience with the two methods.
 
-\subsection{A subsection}
-This is an example of a sub-section.
+\section{Main functions}
+The datasets consists only XML files which, being of a document-oriented database, is structured into attributes attributed to each element of the file.
+Being oriented towards use in HTML, i.e.
+a website, the attributes contain ascii characters, punctuation, numbers and HTML tags that we don't want to be there.
+For this we designed the function cleanBody, meant to clean the text gained from the XML-documents.
+Additionally a function to parse the XML files was required, for which we created XmlParser.
+Lastly, we created a general function that would perform the duties of putting out the results of the mapper function; mapper\_core.
+This section explains their implementations, details the modules imported and describes the bash-script used to run our python-scripts:
 
-% --RESEARCH METHOD--
-\section{Research Method}
-Present your research method and/or design here. 
-In \cite{Hevner2010-yw}, the authors discuss design science research.
+\subsection{cleanBody}
+The cleanBody function formats strings to be parseable by python interpreters.
+The function removes case sensitivity, ascii characters, HTML formatting, and treats anything separated by blanked space or / as separated words.
+This simple implementation of text formatting will affect the results of some tasks.
+For instances the name "Jens-Petter" will be interpreted as the word "jenspetter" and the filepath /documents/folder/file.extension will be interpreted as the words "documents", "folder" and "fileextension".
+\\
+The function takes a string as input, formats it and outputs a list of all the words split by the string.split(" ") function.
+It uses the sub-function of the open source re module to remove HTML-tags and ascii function that is inherent starting with in python 3 to convert all characters to parse-able ascii text.
+The symbols in ignore\_char, which are characters we are not considering is defined by the builtin string functions string.punctuation and string.digits.
+\begin{lstlisting}[language=Python, caption=cleanBody function]
+def cleanBody(body):
+    body = body.lower()
+    body = ascii(body)
+    body = sub("<.+?>","",body)
+    body = body.replace("/", " ")
+    body = body.strip()
 
-Sometimes, you need to use code to illustrate your technical implementations.
-Using \texttt{lstlisting} can help you with that:
+    for i in ignore_char:
+        	body = body.replace(i, "")
 
-\begin{lstlisting}[caption=Displaying Hello World in JavaScript]
-console.log("Hello World!");
+    body = body.split(" ")
+
+    return body
+\end{lstlisting}
+\subsection{Mapper Core}
+mapper\_core is the core of the mapper function; it prints out the relevant data in a format parseable by Hadoop.
+It functions through three modes, as determined by the parameter mode: "single", "double", and "triple".
+
+\begin{itemize}
+  \item Single: Assumes input "words" is a list of words to print. Prints word in words as (word, 1). Ignores empty strings and spaces.
+  \item Double: Assumes input "words" is two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
+  \item Triple: Assumes input "words" is three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
+\end{itemize}
+
+\begin{lstlisting}[language=Python, caption=mapper\_core function]
+def mapper_core(words, mode="single"):
+    if mode == "single":
+        for word in words:
+            if word not in ["", " "]:
+              print("%s %s" %(word,1)) #Emit the word
+
+    elif mode == "double":
+        in1, in2 = words
+        for word, count in zip(in1,in2):
+            if word not in ["", " "]:
+                print("%s %s" %(word,count)) #emit the words
+
+    elif mode == "triple":
+        in1, in2,in3  = words
+        for id, score, title in zip(in1,in2,in3):
+            print("%s %s %s" %(id,score, title)) #emit the words
+
 \end{lstlisting}
 
-You might also want to display a formula, equation, stats, or other types of information requiring a math "mode" in \LaTeX.
+\subsection{xmlparser}
+The xmlparser function parses an xml using the open-source xml.etree.ElementTree.
+For normal use it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
+Although parsing an entire XML-file takes up significant memory, this method fits our dataset.
+It has been separated out as a function so it may be easily replaced by other methods more fit for large files.
+The input for this function is a XML-file and the output is a parsed XML-file.
 
-% In-line using dollar signs
-$E=mc^2$
+\begin{lstlisting}[language=Python, caption=xmlparser function]
+def xmlparser(infile):
+    if not isinstance(infile, str):
+        infile = infile.detach()
+    mytree = ET.parse(infile)
+    myroot = mytree.getroot()
+    return myroot
+\end{lstlisting}
 
-% A free-standing formula with caption
-\begin{figure}[h]
-\[ E = m c^2 \]
-\caption{Mass-energy equivalence}
-\end{figure}
+\subsection{Import sys}
+The sys module is an open-source, built in python function that allows us to add to the module search path with sys.path.append(\'../\'), enabling finding ProjectFunctions in a parallel folder, and read in the input for our mapper function and reduce function using sys.stdin.
+\begin{lstlisting}[language=Python, caption=Import for sys]
+import sys
+sys.path.append(\'../\') #allows access functions in parallel folder
+import ProjectFunctions.functions as proj
+\end{lstlisting}
 
-% --FINDINGS/RESULTS--
-\section{Findings/Results}
-Present your findings/results! 
-It may be in the form of a table, such as in the case of Table \ref{tab:example}.
-Upload data to Github \cite{Github_undated-kr}.
+\subsection{Import xml.etree.ElementTree}
+ElementTree is a part of the xml open-source library.
+XML is an inherently hierarchical data format, being document-oriented, and is naturally represented using a tree-like structure.
+By using the library ElementTree will represent the XML document as a tree, and elements of the tree is represented as single nodes.
+\begin{lstlisting}[language=Python, caption=Import for ElementTree]
+import xml.etree.ElementTree as ET
+\end{lstlisting}
 
-\begin{table}[ht]
-\centering
-\begin{tabular}{|l|l|l|}
-\hline
-\textbf{Condition} & \textbf{n} & \textbf{p} \\
-\hline
-A & 5 & 0.1 \\
-A & 5 & 0.1 \\
-\hline
-\end{tabular}
-\caption{Table caption}
-\end{table}
+\subsection{Import re.sub}
+re.sub is an open-source module we use in cleanBody to remove HTML-tags by removing anything that appears between two chevrons.
+\begin{lstlisting}[language=Python, caption=Import for re.sub]
+from re import sub
+\end{lstlisting}
 
-% --DISCUSSION--
-\section{Discussion}
-A discussion of your findings, results and previous research goes here, perhaps with a reference to Figure \ref{fig:figure_label}.
-
-\begin{figure}[!h]
-\centering
-\includegraphics[width=0.5\linewidth]{images/sample_image.png}
-\caption{Image caption}
-\label{fig:figure_label}
-\end{figure}
-
-% --CONCLUSION--
-\section{Conclusion}
-Briefly conclude your study, and present thoughts on implications and further work.
-
-\begin{itemize}
-	\item One idea on further work;
-	\item A second idea as well;
-\end{itemize}
-
-% --REFERENCES--
-\bibliography{references} % <-- This line will generate the bibliography list automatically
-\bibliographystyle{IEEEtran} % <-- Change this line if you want to use a different citation style
+\subsection{Bash-script}
+As an example of files being run, this bash-script that was used while testing out scripts is provided.
+It was used on a windows PC, meaning scripts had to be converted to unix code.
+It automatically names, cleans, and saves outputs locally.
+In this example task 4 index is being run.
+Other examples are 2c using task=2c and taskname=TopMiners and xmlsource=users.
+\lstinputlisting[title=bash-script for a windows-based environment]{runscript.sh}
 

### 2020-02-17 OldExam_Article/main.tex

% Do not modify these
\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

% -- Insert any custom LaTeX packages here --

% \package{natbib} % <-- Required for the Chicago citation style
% \package{apacite} % <-- Required for the APA citation style
% If you decide to use one of the styles above, remember to change the \bibliographystyle{} at the bottom of the document too!

\usepackage{listings} % <-- Required if you want to display program source code in your paper.
\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
    }
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\urlstyle{same}

% -- End of custom LaTeX packages --

% Fill in your title
\title{Exploring Bitcoin }

% Do not modify the author tag below, just let it be blank
\author{}

% Fill in assignment abstract
\begin{abstract}
In this assignment we parsed a dataset, in the form of XMLs, through a Hadoop- and Pig apache. We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from Bitcoin stack exchange.

\end{abstract}

% Do not modify the following two lines
\lstset{style=mystyle}
\begin{document}
\include{cover}

% Insert data for the hand-in's cover page
\makecoverpage{
	master_of 		 = \par{Applied Computer Science},  % Use either: Applied Computer Science | Human-Computer Interaction
	assignment_title = \par{ Exploring Bitcoin} ,  % Title of your assignment
	course_code    	 = \par{MA120},  % Course code (ex. MA110)
	course_name      = \par{Big Data},  % Course name (ex. Systems Development)
	due_date		 = \par{18.October 2019},  % Due date
	student_name     = \par{Theodor Midtbø Alstad ; Howie Chen},  % Your name (or names, if group – separate names with ; semicolon)
	student_number   = \par{865317 ; 866354},  % Your student ID number (or numbers, if group – separate ID numbers with ; semicolon)
	group_size		 = 2, % Number of group members (used for the declaration text)
}

% Do not modify the following two lines
\flushbottom
\maketitle

\tableofcontents
\newpage
% --INTRODUCTION--
\section{Introduction}
This report is of a structure where each task is independent and separately reported, frequently referring to each other due to their similarity. Each contains our assumptions about what the task is asking for, implementation, and any notes/reflections if necessary, opting to add notes/reflection more than necessary rather than less than necessary.\\
We chose to work together because both of us have python background, choosing python as main programming language. We explored a Bitcoin StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/bitcoin.stackexchange.com.7z} (accessed 16.10.2019) through Hadoop and Pig.\\
Hadoop is used to store and process big data, it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs. Hadoop provides a framework which allow users to write and test distributed systems and does not rely on hardware to provide fault tolerance, making it less apt for our small-scale applications, yet we use it for the experience. Pig is a MapReduce abstraction, working on Hadoop methods, that we use in some tasks due to its efficiency. We have elected to use both pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both show our ability to employ both methods and get experience with the two methods.

% --FUNCTIONS %-- 
\section{Main functions}
The datasets consists only XML files which, being of a document-oriented database, is structured into attributes attributed to each element of the file. Being oriented towards use in HTML, i.e. a website, the attributes contain ascii characters, punctuation, numbers and HTML tags that we don't want to be there. For this we designed the function cleanBody, meant to clean the text gained from the XML-documents. Additionally a function to parse the XML files was required, for which we created XmlParser. Lastly, we created a general function that would perform the duties of putting out the results of the mapper function; mapper\_core. This section explains their implementations, details the modules imported and describes the bash-script used to run our python-scripts:

\subsection{cleanBody}
The cleanBody function formats strings to be parseable by python interpreters. The function removes case sensitivity, ascii characters, HTML formatting, and treats anything separated by blanked space or / as separated words. This simple implementation of text formatting will affect the results of some tasks. For instances the name "Jens-Petter" will be interpreted as the word "jenspetter" and the filepath /documents/folder/file.extension will be interpreted as the words "documents", "folder" and "fileextension". \\
The function takes a string as input, formats it and outputs a list of all the words split by the string.split(" ") function.
It uses the sub-function of the open source re module to remove HTML-tags and ascii function that is inherent starting with in python 3 to convert all characters to parse-able ascii text. The symbols in ignore\_char, which are characters we are not considering is defined by the builtin string functions string.punctuation and string.digits.

\begin{lstlisting}[language=Python, caption=cleanBody function]
def cleanBody(body):
    body = body.lower()
    body = ascii(body)
    body = sub("<.+?>","",body)
    body = body.replace("/", " ")
    body = body.strip()

    for i in ignore_char:
        	body = body.replace(i, "")

    body = body.split(" ")

    return body
\end{lstlisting}
\subsection{Mapper Core}
mapper\_core is the core of the mapper function; it prints out the relevant data in a format parseable by Hadoop. It functions through three modes, as determined by the parameter mode: "single", "double", and "triple".

\begin{itemize}
  \item Single: Assumes input "words" is a list of words to print. Prints word in words as (word, 1). Ignores empty strings and spaces.
  \item Double: Assumes input "words" is two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
  \item Triple: Assumes input "words" is three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
\end{itemize}

\begin{lstlisting}[language=Python, caption=mapper\_core function]
def mapper_core(words, mode="single"):
    if mode == "single":
        for word in words:
            if word not in ["", " "]:
              print("%s %s" %(word,1)) #Emit the word

    elif mode == "double":
        in1, in2 = words
        for word, count in zip(in1,in2):
            if word not in ["", " "]:
                print("%s %s" %(word,count)) #emit the words

    elif mode == "triple":
        in1, in2,in3  = words
        for id, score, title in zip(in1,in2,in3):
            print("%s %s %s" %(id,score, title)) #emit the words

\end{lstlisting}

\subsection{xmlparser}
The xmlparser function parses an xml using the open-source xml.etree.ElementTree. For normal use it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
Although parsing an entire XML-file takes up significant memory, this method fits our dataset. It has been separated out as a function so it may be easily replaced by other methods more fit for large files. The input for this function is a XML-file and the output is a parsed XML-file.

\begin{lstlisting}[language=Python, caption=xmlparser function]
def xmlparser(infile):
    if not isinstance(infile, str):
        infile = infile.detach()
    mytree = ET.parse(infile)
    myroot = mytree.getroot()
    return myroot
\end{lstlisting}

\subsection{Import sys}
The sys module is an open-source, built in python function that allows us to add to the module search path with sys.path.append(\'../\'), enabling finding ProjectFunctions in a parallel folder, and read in the input for our mapper function and reduce function using sys.stdin.
\begin{lstlisting}[language=Python, caption=Import for sys]
import sys
sys.path.append(\'../\') #allows access functions in parallel folder
import ProjectFunctions.functions as proj
\end{lstlisting}

\subsection{Import xml.etree.ElementTree}
ElementTree is a part of the xml open-source library. XML is an inherently hierarchical data format, being document-oriented, and is naturally represented using a tree-like structure. By using the library ElementTree will represent the XML document as a tree, and elements of the tree is represented as single nodes. 
\begin{lstlisting}[language=Python, caption=Import for ElementTree]
import xml.etree.ElementTree as ET
\end{lstlisting}

\subsection{Import re.sub}
re.sub is an open-source module we use in cleanBody to remove HTML-tags by removing anything that appears between two chevrons.
\begin{lstlisting}[language=Python, caption=Import for re.sub]
from re import sub
\end{lstlisting}

\subsection{Bash-script}
As an example of files being run, this bash-script that was used while testing out scripts is provided. It was used on a windows PC, meaning scripts had to be converted to unix code. It automatically names, cleans, and saves outputs locally. In this example task 4 index is being run. Other examples are 2c using task=2c and taskname=TopMiners and xmlsource=users.
\lstinputlisting[title=bash-script for a windows-based environment]{runscript.sh}

% --TASK1--
\section{Task 1 Warmup}
%This part of the task is about get to know how hadoop- and pig apache works and how to parse XML  files throught python code. 
\subsection{WordCount}
\textbf{Assumption}: Count the words in body of questions, identified by PostTypeID="1", in \textit{Posts.xml}. The result should be a list of each word and how many times it occurs in the bodies of questions. \\ \\
\textbf{Implementation}: The mapper uses the xmlparser function to parse an XML-file, iterates through all rows in parsed file, cleans text using the cleanBody function and prints output for the reducer script by using the mapper\_core function.
The reducer receives the mapper output, parses it and iterates through the parsed lines. A counter variable is used to track repeated words, outputting the word with the counter when the word stops repeating. \\ \\
\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things as words that clearly are not. See line 7 in 1a\_output for examples; what is possibly a<br>, an html line break element, is interpreted as the word abr. \\ \\

\lstinputlisting[firstline=500, lastline=510, title=1a\_output]{output1a.txt}

\subsection{Unique words}
\textbf{Assumption}: Write a MapReduce job which outputs unique words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}. The result should be a list of each word as it appears in the titles of questions. \\ \\
\textbf{Implementation}: This MapReduce job functions as 1a WordCount does, except it does not count the words and it looks through the titles instead of the bodies. \\ \\
\textbf{Notes/Reflection}: Here again the choices made building the cleanBody function affects the output.
\lstinputlisting[firstline=500,lastline=510,title=1b\_output]{output1b.txt}

\subsection{MoreThan10}
\textbf{Assumption}: Write a simple python script to check the amount of words in titles of posts in \textit{Posts.xml}. The result should be a count of how many titles have more than 10 words. \\ \\
\textbf{Implementation}: The mapper functions as the mapper in 1a WordCount, except it keeps a counter for the titles of more than 10 words and it outputs the final counter instead of using mapper\_core.
The reducer receives the mapper outputs and sums them up. \\ \\
\textbf{Notes/Reflection}: This MapReduce job is simpler, the reducer is unnecessary outside an environment with clusters.
\lstinputlisting[firstline=1,lastline=1,title=1c\_output]{output1c.txt}

\subsection{Stopwords}
\textbf{Assumption}: Write a simple python script based on task 1a to exclude \href{https://raw.githubusercontent.com/naimdjon/stopwords/master/stopwords.txt}{stopwords}: from body of questions, identified by PostTypeID="1", in \textit{Posts.xml}. The output should be a word count excluding any stop words. \\ \\
\textbf{Implementation}: This MapReduce job functions as 1a WordCount does, except it has a section for the iterative removal of stopwords, as defined in \href{https://raw.githubusercontent.com/naimdjon/stopwords/master/stopwords.txt}{StopWords.txt}. \\ \\
\textbf{Notes/Reflection}: Given how we built cleanBody, we chose to remove the apostrophes (') from the stopwords, turning words like "we're" to "were".
\lstinputlisting[firstline=500,lastline=509,title=1d\_output]{output1d.txt}

\subsection{Pig top 10}
\textbf{Assumption}: Write a pig script to select top 10 listed words after removing the stopwords from \textit{Posts.xml}. The output should be a list of the top 10 listed words and the corresponding occurrence count.\\ \\
\textbf{Implementation}: Given this task being based on 1d StopWords, the mapper and reducer are the same for both tasks. Our pig loaded the output from the MapReduce job, ordered it by count, limited it to 10 elements and stored it into a text file: 1ePig\_Output.txt. \\ \\
\textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an hdfs cluster as opposed to a local storage location.
\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{output1e.txt}

\subsection{Tags}
\textbf{Assumption}: Write a MapReduce job to create a dictionary over unique tags in \textit{Posts.xml}. The result should be a list of unique tags.\\ \\
\textbf{Implementation}: This MapReduce job functions similarly to 1a WordCount, except it has to be aware of whether the post has a tag at all or not, being implemented when tags are extracted from the row. \\ \\
\textbf{Notes/Reflection}: The tags are separated by chevrons, and would be fused by cleanBody, so we elected to replace them with spaces. Some of the posts lacked any tag attribute, so we elected to pass over those.
\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{output1f.txt}

% --TASK2--
\section{Task 2 Discover}
%This part of the task is about to looking through several

\subsection{Counting}
\textbf{Assumption}: Write a MapReduce job to count the total unique users there are in \textit{Users.xml}. The result should be a count of how many unique users there are.\\ \\
\textbf{Implementation}: This MapReduce job functions similarly to 1c MoreThan10, except it counts all unique users instead of titles with more than 10 words. \\ \\
\textbf{Notes/Reflection}: We interpreted "unique user" as a user with a unique Id attribute.
\lstinputlisting[firstline=1,lastline=1,title=2a\_output]{output2a.txt}

\subsection{Unique users}
\textbf{Assumption}: Write a MapReduce job based on 2a Counting to list the unique users in \textit{Users.xml}. The result should be a list containing unique users in the dataset. \\ \\
\textbf{Implementation}: This MapReduce job functions as 2a Counting does, except it outputs all unique users instead of a count of them \\ \\
\textbf{Notes/Reflection}: Here the implementation of cleanBody is modified with a join function as cleanBody returns a list where we want a string. Since usernames can contain spaces, we elected to instead use | as a separator in hadoop.
 \lstinputlisting[firstline=500,lastline=510,title=2b\_output]{output2b.txt}

\subsection{Top miners}
\textbf{Assumption}:Write a pig script or MapReduce job to find top 10 users based on Reputation attribute in \textit{Users.xml}. The result should be a list of the 10 users based with the highest reputation value. \\ \\
\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out name and id, it puts out name and the reputation attribute. Here, reputation is given to mapper\_core as a one-element list (mapper\_core called with arguments (name, [reputation])) due to it looping through its inputs. The reducer is the same as the reducer of 2b Unique users. The pig script functions the same way as in 1e Pig Top 10\\ \\
\textbf{Notes/Reflection}: We elected here to use pig to order the MapReduce output in order to get experience.
\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{output2c.txt}

\subsection{Top questions}
\textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on the Score attribute. The result should be a list containing the top 10 questions, showing id, question, and score.\\ \\
\textbf{Implementation}: This mapper job functions similarly to 2c Top miners except it puts out 3 parsed attributes using the "triple"-mode of mapper\_core. The reducer performs the reduction and ordering, finding the 10 highest score values. It does this by inserting every input into a list instead of printing it, using pythons standard function string.sort to order it. It then iterates through the 10 highest values to give an output.\\ \\
\textbf{Notes/Reflection}: The reducer could potentially be improved by only keeping 10 elements in the list at once, changing them out as higher scores were encountered.
\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{output2d.txt}

\subsection{Favorite questions}
\textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on FavouriteCount attribute. The result should be a list containing the top 10 questions, showing  id, question and the favourite count. \\ \\
\textbf{Implementation}: This MapReduce job is the same as 2d Top questions, except it extracts the FavoriteCount-attribute instead of the score \\ \\
\textbf{Notes/Reflection}: Here, like 1f Tags, some posts had to be skipped due to their lacking any FavoriteCount-attribute.
\lstinputlisting[firstline=1,lastline=10,title=2e\_output]{output2e.txt}

\subsection{Average answers}
\textbf{Assumption}: Write a MapReduce job that calculates the average number of answers per question. The result should be a calculated average of all AnswerCount attributes. \\ \\
\textbf{Implementation}: This mapper functions similarly to  1c MoreThan10, except for having two counters, one for score and the other for users parsed, which are averaged at the end. The reducer is the same as the reducer in 2a Counting \\ \\
\textbf{Notes/Reflection}: We have elected to not limit the amount of decimals.
\lstinputlisting[firstline=1,lastline=10,title=2f\_output]{output2f.txt}

\subsection{Countries}
\textbf{Assumption}: Write a MapReduce job to count the amount of users attributed to a country by the Location attribute in \textit{Users.xml}. The result should be a list of different countries and corresponding users. \\ \\
\textbf{Implementation}: This mapper functions similarly to 1f tags, except instead of cleaning the tags, it uses "|" as a separator, since spaces are part of location. If Location is separated by a \',\' the last part is treated as the country. \\ \\
\textbf{Notes/Reflection}: Because by our judgement locations are typed in by users, we have elected to separate the country out of Location very simply by using \',\' as a separator. Anything after the last \',\' is treated as a country. A location with no \',\' is treated as a country. Locations like "California, USA", "California, United States", and "US" will be interpreted as "usa", "united states", and "us", respectively.
\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{output2g.txt}

\subsection{Names}
\textbf{Assumption}: Write a pig script or MapReduce job to find the 10 most popular names in \textit{Users.xml}. The result should be a list top 10 common names. \\ \\
\textbf{Implementation}: This mapper functions similarly to 2g Countries, except it extracts the DisplayName-attribute in place of the Location-attribute. The reducer functions similarly to 2d Top questions, except it parses differently and has different text formatting for the output due to the decrease from 3 to 2 arguments \\ \\
\textbf{Notes/Reflection}: Here the most common name is User. This is due to our choice of removing numbers in cleanBody, combining User1, User2, User3 etc. The task suggested explicitly that we should split up names by spaces, perhaps wanting to separate out last names from first names. Due to the nature of Displaynames usually not being full legal names, we have elected to interpret a "name" as the full name given in DisplayName.
\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{output2h.txt}

\subsection{Answers}
\textbf{Assumption}: Write a python script to find how many questions, identified by PostTypeID="1", in \textit{Posts.xml} have at least one answer based on attribute AnswerCount. The result should be a count of how many questions have been answered.  \\ \\
\textbf{Implementation}: This mapper functions in the same way as 1c MoreThan10 except it checks whether AnswerCount is larger than or equal to 1 instead of whether the title word length is larger than 10.
\lstinputlisting[firstline=1,lastline=10,title=2i\_output]{output2i.txt}

% --TASK3--
\section{Task 3 Numbers}

\subsection{Bigram}
\textbf{Assumption}: We chose to write a MapReduce job to find the most common pair of adjacent words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}. A bigram is a combination of two words in a sequence. For instance the sentence "Big data is big" contains the bigrams "Big data", "data is", and "is big". The result should be the most common bigram along with a count of how many times it occurs. \\ \\
\textbf{Implementation}: This MapReduce is exactly the same as 1a WordCount, except we output each bigram in the body instead of each word. Because of this we he had to forego the mapper\_core for a print function inside a loop looping through every bigram. The reducer finds the most common bigram by iteratively comparing each elements second element (the bigrams count) against a variable declared maximum. \\ \\
\textbf{Notes/Reflection}: In the print-loop we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{output3a.txt}

\subsection{Trigram}
\textbf{Assumption}: Perform the same task as in 3a Bigram, except operate with trigrams (sequences of 3 words as opposed to 2). The result should be the most common trigram. \\ \\
\textbf{Implementation}: This is exactly the same as 3a Bigram, except we output trigrams instead of bigrams. \\ \\
\textbf{Notes/Reflection}: The mapper, as in 3a Bigram, limited the print-loop to range(len(words)-2) and printed words[i], words[i+1], and words[i+2].
\lstinputlisting[firstline=1,lastline=10,title=3b\_output]{output3b.txt}

\subsection{Combiner}
\textbf{Assumption}: Perform the same task as in 1a WordCount, except add a combiner before the mapper sends information to the reducer. The result should be the same as in 1a WordCount, but the volume of the data transfer should be smaller. \\ \\
\textbf{Implementation} The MapReduce function is the same as in 1a WordCount, with a combiner ahead of the print function in the mapper. \\ \\
\textbf{Notes/Reflection}: Having a combiner in a MapReduce job saves bandwidth and computational strain by decreasing the volume of data sent from the mapper. This is less relevant in our case, working with relatively small datasets.
\lstinputlisting[firstline=1,lastline=10,title=3c\_output]{output1a.txt}

\subsection{Useless}
\textbf{Assumption}: Write a MapReduce job to find how many times the word "useless" in occurs in the bodies of questions, identified by PostTypeID="1", in \textit{Posts.xml}. The result should be a count of how many times the word useless occurs. \\ \\
\textbf{Implementation}: This mapper functions similarly to 1c MoreThan10 and 2i Answers, except instead of checking for titles with more words than 10 or whether AnswerCount is larger than or equal to 1, it counts whether the word "useless" occurs in the body. \\ \\
\lstinputlisting[firstline=1,lastline=10,title=3d\_output]{output3d.txt}

% --TASK4--
\section{Task 4 Search engine}
\subsection{Title index}
\textbf{Assumption}: Write MapReduce job to create index over titles, bodies and answers of questions in \textit{Posts.xml}. The result should be a simple index that lists posts words appear in by their Id's. \\ \\
\textbf{Implementation}: This mapper function parses through all rows in posts.xml. It then forks over whether PostTypeId is 1 or 2, i.e. whether it is an answer or question, extracting the relevant id, body and title from the row. It contains a combiner to speed up the process, removing duplicates. The reducer parses the input and iterates through all the lines. It uses two variables to know what the last word and associated Id was, skipping the word if both are the same, adding the Id to a list if \textit{only} the word is the same, and putting out the word with an associated list of Id's if neither is the same, i.e. it has finished working with the word. \\ \\
\textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary, since we are working with small file-sizes.
\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{output4a.txt}

\section{Conclusion}
Through this assignment we gained experience in using MapReduce jobs and pig scripts. We parsed XML-documents and extracted specific information we were looking for to be formatted to an output to each tasks.

% Do not modify this last lines
\end{document}

### 2020-02-17 Article_Final/main.tex
latex endringer

@@
 \usepackage[T1]{fontenc}
+\usepackage{sectsty}
+\renewcommand{\thesection}{\Roman{section}}
+\renewcommand{\thesubsection}{\Alph{subsection}}
 
@@
 \end{lstlisting}
-\subsection{Mapper Core}
+\subsection{\emph{Mapper Core}}
 mapper\_core is the core of the mapper function; it prints out the relevant data in a format parseable by Hadoop.
@@
 
-\subsection{xmlparser}
-The xmlparser function parses an xml using the open-source xml.etree.ElementTree.
+\subsection{XML Parser}
+The XML Parser function parses an xml using the open-source xml.etree.ElementTree.
 For normal use it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
@@
 Other examples are 2c using task=2c and taskname=TopMiners and xmlsource=users.
-\lstinputlisting[title=bash-script for a windows-based environment]{runscript.sh}
+\lstinputlisting[title=bash-script for a windows-based environment]{Code_Files/runBasis_windows.sh}
+
+% --TASK1--
+\section{Task 1 Warmup}
+%This part of the task is about get to know how hadoop- and pig apache works and how to parse XML  files throught python code. 
+\subsection{WordCount}
+\textbf{Assumption}: Count the words in body of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
+The result should be a list of each word and how many times it occurs in the bodies of questions.
+\\ \\
+\textbf{Implementation}: The mapper uses the xmlparser function to parse an XML-file, iterates through all rows in parsed file, cleans text using the cleanBody function and prints output for the reducer script by using the mapper\_core function.
+The reducer receives the mapper output, parses it and iterates through the parsed lines.
+A counter variable is used to track repeated words, outputting the word with the counter when the word stops repeating.
+\\ \\
+\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things as words that clearly are not.
+See line 7 in 1a\_output for examples; what is possibly a<br>, an html line break element, is interpreted as the word abr.
+\\ \\
+
+\lstinputlisting[firstline=500, lastline=510, title=1a\_output]{output1a.txt}
+
+\subsection{Unique words}
+\textbf{Assumption}: Write a MapReduce job which outputs unique words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
+The result should be a list of each word as it appears in the titles of questions.
+\\ \\
+\textbf{Implementation}: This MapReduce job functions as 1a WordCount does, except it does not count the words and it looks through the titles instead of the bodies. \\ \\
+\textbf{Notes/Reflection}: Here again the choices made building the cleanBody function affects the output.
+\lstinputlisting[firstline=500,lastline=510,title=1b\_output]{output1b.txt}
+
+\subsection{MoreThan10}
+\textbf{Assumption}: Write a simple python script to check the amount of words in titles of posts in \textit{Posts.xml}. The result should be a count of how many titles have more than 10 words. \\ \\
+\textbf{Implementation}: The mapper functions as the mapper in 1a WordCount, except it keeps a counter for the titles of more than 10 words and it outputs the final counter instead of using mapper\_core.
+The reducer receives the mapper outputs and sums them up. \\ \\
+\textbf{Notes/Reflection}: This MapReduce job is simpler, the reducer is unnecessary outside an environment with clusters.
+\lstinputlisting[firstline=1,lastline=1,title=1c\_output]{output1c.txt}
+
+\subsection{Stopwords}
+\textbf{Assumption}: Write a simple python script based on task 1a to exclude \href{https://raw.githubusercontent.com/naimdjon/stopwords/master/stopwords.txt}{stopwords}: from body of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
+The output should be a word count excluding any stop words.
+\\ \\
+\textbf{Implementation}: This MapReduce job functions as 1a WordCount does, except it has a section for the iterative removal of stopwords, as defined in \href{https://raw.githubusercontent.com/naimdjon/stopwords/master/stopwords.txt}{StopWords.txt}.
+\\ \\
+\textbf{Notes/Reflection}: Given how we built cleanBody, we chose to remove the apostrophes (') from the stopwords, turning words like "we're" to "were".
+\lstinputlisting[firstline=500,lastline=509,title=1d\_output]{output1d.txt}
+
+\subsection{Pig top 10}
+\textbf{Assumption}: Write a pig script to select top 10 listed words after removing the stopwords from \textit{Posts.xml}.
+The output should be a list of the top 10 listed words and the corresponding occurrence count.\\ \\
+\textbf{Implementation}: Given this task being based on 1d StopWords, the mapper and reducer are the same for both tasks.
+Our pig loaded the output from the MapReduce job, ordered it by count, limited it to 10 elements and stored it into a text file: 1ePig\_Output.txt.
+\\ \\
+\textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an hdfs cluster as opposed to a local storage location.
+\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{output1e.txt}
+
+\subsection{Tags}
+\textbf{Assumption}: Write a MapReduce job to create a dictionary over unique tags in \textit{Posts.xml}. The result should be a list of unique tags.\\ \\
+\textbf{Implementation}: This MapReduce job functions similarly to 1a WordCount, except it has to be aware of whether the post has a tag at all or not, being implemented when tags are extracted from the row.
+\\ \\
+\textbf{Notes/Reflection}: The tags are separated by chevrons, and would be fused by cleanBody, so we elected to replace them with spaces.
+Some of the posts lacked any tag attribute, so we elected to pass over those.
+\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{output1f.txt}
+
+% --TASK2--
+\section{Task 2 Discover}
+%This part of the task is about to looking through several
+
+\subsection{Counting}
+\textbf{Assumption}: Write a MapReduce job to count the total unique users there are in \textit{Users.xml}. The result should be a count of how many unique users there are.\\ \\
+\textbf{Implementation}: This MapReduce job functions similarly to 1c MoreThan10, except it counts all unique users instead of titles with more than 10 words. \\ \\
+\textbf{Notes/Reflection}: We interpreted "unique user" as a user with a unique Id attribute.
+\lstinputlisting[firstline=1,lastline=1,title=2a\_output]{output2a.txt}
+
+\subsection{Unique users}
+\textbf{Assumption}: Write a MapReduce job based on 2a Counting to list the unique users in \textit{Users.xml}. The result should be a list containing unique users in the dataset. \\ \\
+\textbf{Implementation}: This MapReduce job functions as 2a Counting does, except it outputs all unique users instead of a count of them \\ \\
+\textbf{Notes/Reflection}: Here the implementation of cleanBody is modified with a join function as cleanBody returns a list where we want a string.
+Since usernames can contain spaces, we elected to instead use | as a separator in hadoop.
+ \lstinputlisting[firstline=500,lastline=510,title=2b\_output]{output2b.txt}
+
+\subsection{Top miners}
+\textbf{Assumption}:Write a pig script or MapReduce job to find top 10 users based on Reputation attribute in \textit{Users.xml}.
+The result should be a list of the 10 users based with the highest reputation value.
+\\ \\
+\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out name and id, it puts out name and the reputation attribute.
+Here, reputation is given to mapper\_core as a one-element list (mapper\_core called with arguments (name, [reputation])) due to it looping through its inputs.
+The reducer is the same as the reducer of 2b Unique users.
+The pig script functions the same way as in 1e Pig Top 10\\ \\
+\textbf{Notes/Reflection}: We elected here to use pig to order the MapReduce output in order to get experience.
+\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{output2c.txt}
+
+\subsection{Top questions}
+\textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on the Score attribute.
+The result should be a list containing the top 10 questions, showing id, question, and score.\\ \\
+\textbf{Implementation}: This mapper job functions similarly to 2c Top miners except it puts out 3 parsed attributes using the "triple"-mode of mapper\_core.
+The reducer performs the reduction and ordering, finding the 10 highest score values.
+It does this by inserting every input into a list instead of printing it, using pythons standard function string.sort to order it.
+It then iterates through the 10 highest values to give an output.\\ \\
+\textbf{Notes/Reflection}: The reducer could potentially be improved by only keeping 10 elements in the list at once, changing them out as higher scores were encountered.
+\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{output2d.txt}
+
+\subsection{Favorite questions}
+\textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on FavouriteCount attribute.
+The result should be a list containing the top 10 questions, showing  id, question and the favourite count.
+\\ \\
+\textbf{Implementation}: This MapReduce job is the same as 2d Top questions, except it extracts the FavoriteCount-attribute instead of the score \\ \\
+\textbf{Notes/Reflection}: Here, like 1f Tags, some posts had to be skipped due to their lacking any FavoriteCount-attribute.
+\lstinputlisting[firstline=1,lastline=10,title=2e\_output]{output2e.txt}
+
+\subsection{Average answers}
+\textbf{Assumption}: Write a MapReduce job that calculates the average number of answers per question. The result should be a calculated average of all AnswerCount attributes. \\ \\
+\textbf{Implementation}: This mapper functions similarly to  1c MoreThan10, except for having two counters, one for score and the other for users parsed, which are averaged at the end.
+The reducer is the same as the reducer in 2a Counting \\ \\
+\textbf{Notes/Reflection}: We have elected to not limit the amount of decimals.
+\lstinputlisting[firstline=1,lastline=10,title=2f\_output]{output2f.txt}
+
+\subsection{Countries}
+\textbf{Assumption}: Write a MapReduce job to count the amount of users attributed to a country by the Location attribute in \textit{Users.xml}.
+The result should be a list of different countries and corresponding users.
+\\ \\
+\textbf{Implementation}: This mapper functions similarly to 1f tags, except instead of cleaning the tags, it uses "|" as a separator, since spaces are part of location.
+If Location is separated by a \',\' the last part is treated as the country.
+\\ \\
+\textbf{Notes/Reflection}: Because by our judgement locations are typed in by users, we have elected to separate the country out of Location very simply by using \',\' as a separator.
+Anything after the last \',\' is treated as a country.
+A location with no \',\' is treated as a country.
+Locations like "California, USA", "California, United States", and "US" will be interpreted as "usa", "united states", and "us", respectively.
+\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{output2g.txt}
+
+\subsection{Names}
+\textbf{Assumption}: Write a pig script or MapReduce job to find the 10 most popular names in \textit{Users.xml}. The result should be a list top 10 common names. \\ \\
+\textbf{Implementation}: This mapper functions similarly to 2g Countries, except it extracts the DisplayName-attribute in place of the Location-attribute.
+The reducer functions similarly to 2d Top questions, except it parses differently and has different text formatting for the output due to the decrease from 3 to 2 arguments \\ \\
+\textbf{Notes/Reflection}: Here the most common name is User.
+This is due to our choice of removing numbers in cleanBody, combining User1, User2, User3 etc.
+The task suggested explicitly that we should split up names by spaces, perhaps wanting to separate out last names from first names.
+Due to the nature of Displaynames usually not being full legal names, we have elected to interpret a "name" as the full name given in DisplayName.
+\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{output2h.txt}
+
+\subsection{Answers}
+\textbf{Assumption}: Write a python script to find how many questions, identified by PostTypeID="1", in \textit{Posts.xml} have at least one answer based on attribute AnswerCount.
+The result should be a count of how many questions have been answered.
+\\ \\
+\textbf{Implementation}: This mapper functions in the same way as 1c MoreThan10 except it checks whether AnswerCount is larger than or equal to 1 instead of whether the title word length is larger than 10.
+\lstinputlisting[firstline=1,lastline=10,title=2i\_output]{output2i.txt}
+
+% --TASK3--
+\section{Task 3 Numbers}
+
+\subsection{Bigram}
+\textbf{Assumption}: We chose to write a MapReduce job to find the most common pair of adjacent words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
+A bigram is a combination of two words in a sequence.
+For instance the sentence "Big data is big" contains the bigrams "Big data", "data is", and "is big".
+The result should be the most common bigram along with a count of how many times it occurs.
+\\ \\
+\textbf{Implementation}: This MapReduce is exactly the same as 1a WordCount, except we output each bigram in the body instead of each word.
+Because of this we he had to forego the mapper\_core for a print function inside a loop looping through every bigram.
+The reducer finds the most common bigram by iteratively comparing each elements second element (the bigrams count) against a variable declared maximum.
+\\ \\
+\textbf{Notes/Reflection}: In the print-loop we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
+\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{output3a.txt}
+
+\subsection{Trigram}
+\textbf{Assumption}: Perform the same task as in 3a Bigram, except operate with trigrams (sequences of 3 words as opposed to 2). The result should be the most common trigram. \\ \\
+\textbf{Implementation}: This is exactly the same as 3a Bigram, except we output trigrams instead of bigrams. \\ \\
+\textbf{Notes/Reflection}: The mapper, as in 3a Bigram, limited the print-loop to range(len(words)-2) and printed words[i], words[i+1], and words[i+2].
+\lstinputlisting[firstline=1,lastline=10,title=3b\_output]{output3b.txt}
+
+\subsection{Combiner}
+\textbf{Assumption}: Perform the same task as in 1a WordCount, except add a combiner before the mapper sends information to the reducer.
+The result should be the same as in 1a WordCount, but the volume of the data transfer should be smaller.
+\\ \\
+\textbf{Implementation} The MapReduce function is the same as in 1a WordCount, with a combiner ahead of the print function in the mapper. \\ \\
+\textbf{Notes/Reflection}: Having a combiner in a MapReduce job saves bandwidth and computational strain by decreasing the volume of data sent from the mapper.
+This is less relevant in our case, working with relatively small datasets.
+\lstinputlisting[firstline=1,lastline=10,title=3c\_output]{output1a.txt}
+
+\subsection{Useless}
+\textbf{Assumption}: Write a MapReduce job to find how many times the word "useless" in occurs in the bodies of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
+The result should be a count of how many times the word useless occurs.
+\\ \\
+\textbf{Implementation}: This mapper functions similarly to 1c MoreThan10 and 2i Answers, except instead of checking for titles with more words than 10 or whether AnswerCount is larger than or equal to 1, it counts whether the word "useless" occurs in the body.
+\\ \\
+\lstinputlisting[firstline=1,lastline=10,title=3d\_output]{output3d.txt}
+
+% --TASK4--
+\section{Task 4 Search engine}
+\subsection{Title index}
+\textbf{Assumption}: Write MapReduce job to create index over titles, bodies and answers of questions in \textit{Posts.xml}.
+The result should be a simple index that lists posts words appear in by their Id's.
+\\ \\
+\textbf{Implementation}: This mapper function parses through all rows in posts.xml.
+It then forks over whether PostTypeId is 1 or 2, i.e.
+whether it is an answer or question, extracting the relevant id, body and title from the row.
+It contains a combiner to speed up the process, removing duplicates.
+The reducer parses the input and iterates through all the lines.
+It uses two variables to know what the last word and associated Id was, skipping the word if both are the same, adding the Id to a list if \textit{only} the word is the same, and putting out the word with an associated list of Id's if neither is the same, i.e.
+it has finished working with the word.
+\\ \\
+\textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary, since we are working with small file-sizes.
+\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{output4a.txt}
+
+\section{Conclusion}
+Through this assignment we gained experience in using MapReduce jobs and pig scripts.
+We parsed XML-documents and extracted specific information we were looking for to be formatted to an output to each tasks.
 

### 2020-02-17 Code/task1/task1a/run1a_windows.sh
adjusted .gitignore to ignore .xml

@@ -5,10 +5,11 @@
 #Simplify task change further
 tasknumb=1a
 taskname=WordCount
+sourceFile=Posts
 
 #Simplify task change
 mapperfile=$tasknumb$taskname.py
-reducerfile="$tasknumb"reducer.py
+reducerfile="$tasknumb"Reducer.py
 outfile=output$tasknumb
 
 #Automatic removal
@@ -19,12 +20,12 @@ apt-get install dos2unix
 dos2unix $mapperfile
 dos2unix $reducerfile
 
-#Main MapReduce function
+#Main MapReduce function call
 hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 -files $mapperfile,$reducerfile \
 -mapper $mapperfile \
 -reducer $reducerfile \
--input posts.xml \
+-input Posts.xml \
 -output $outfile
 
 #Read file and save it locally

### 2020-02-17 Code/task1/task1a/run1a_windows.sh
Lmao

@@ -24,7 +24,7 @@ hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 -files $mapperfile,$reducerfile \
 -mapper $mapperfile \
 -reducer $reducerfile \
--input posts.xml \
+-input Posts.xml \
 -output $outfile
 
 #Read file and save it locally

### 2020-02-17 Code/runBasis_windows.sh
Added a bash-script for each task

@@ -3,9 +3,9 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
-sourceFile = Posts
+taskNumber =
+taskName   =
+sourceFile =
 
 #Simplify task change
 mapperfile  = $taskNumber$taskName.py

### 2020-02-17 Code/task1/ProjectFunctions/functions.py

@@ -1,95 +1,0 @@
-import xml.etree.ElementTree as ET
-import string
-import sys
-from re import sub
-
-#Defines characters to be ignored, 123?{/¤ etc.
-ignore_char = string.digits + string.punctuation
-
-
-
-"""
-cleanBody(body)
-Formats string for mapper function
-non-case sensitive, removes HTML- and ascii formatting, 
-treats anything separeted by blank space or / as separate 
-words. Mispellings, names, filenames, functionnames etc. 
-will be counted as separate words
-
-input:
-  string body : string to be formatted
-
-returns:
-  string body : formatted string
-"""
-def cleanBody(body):
-    body = body.lower()
-    body = ascii(body)
-    body = sub("<.+?>","",body)
-    body = body.replace("/", " ")
-    body = body.strip()
-
-    for i in ignore_char:
-        body = body.replace(i, "")
-
-    body = body.split(" ")
-
-    return body
-
-
-"""
-mapper_core(words, mode="single")
-maps list of words into format acceptable by Hadoop
-has three modes, defined by parameter mode="single":
-  single: 
-    iterates through word in words, prints (word, 1)
-  double:
-    Assumes words is two-length list, separates into in1, in2
-    iterates through word, count in zip(in1, in2), prints them
-  triple
-    assumes words is three-length list, separates into in1, in2, in3
-    iterates through id, score, title in zip(in1, in2, in3), prints them
-
-input:
-  list words : words wanted to be passed into Hadoop
-               if 
-
-returns:
-  None, prints words into format acceptable by Hadoop
-"""
-def mapper_core(words, mode="single"):
-    if mode == "single":
-        for word in words:
-            if word not in ["", " "]:
-              print("%s %s" %(word,1)) #Emit the word
-
-    elif mode == "double":
-        in1, in2 = words
-        for word, count in zip(in1,in2):
-            if word not in ["", " "]:
-                print("%s %s" %(word,count)) #emit the words
-
-    elif mode == "triple":
-        in1, in2,in3  = words
-        for id, score, title in zip(in1,in2,in3):
-            print("%s %s %s" %(id,score, title)) #emit the words
-
-
-"""
-xmlparser(infile):
-Our chosen method for interpreting our dataset. Takes up
-a larger amount of memory for larger filesizes, but is
-fast enough and small enough for application in this dataset
-
-input:  
-  infile : unparsed xml-file
-
-returns:
[…]

### 2020-02-17 Code/task1/task1b/1bUnique.py

@@ -8,8 +8,8 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 """
 xmlmapper(source, infile=sys.stdin)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Lists unique words in xml-files, where the bodies are 
+defined as questions (PostTypeId = 1)
 
 input:
   string source           : xml-tag to extract from
@@ -26,12 +26,12 @@ def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
     # Iterates through each xml-row and extracts data
-    for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+    for titles in parsed:
+        if (titles.attrib["PostTypeId"] == "1"):
+            title = titles.attrib[source]
 
-            words = cleanBody(body)
-
+            words = cleanBody(title)
             mapper_core(words)
 
-xmlmapper("Text")
+xmlmapper("Title")
+

### 2020-02-17 Code/task1/task1b/run1b_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 1b
+taskName   = Unique
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task1/task1c/1cMoreThan10.py

@@ -1,15 +1,15 @@
 #!/usr/bin/python3
 import sys
-sys.path.append('../') #allows access functions in parallel folder
+sys.path.append('../../') #allows access functions in parallel folder
 import ProjectFunctions.functions as proj
 
 cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser
 
 """
-xmlmapper(source, infile=sys.stdin)
-main mapper function, uses cleanBody() and mapper_core()
-Lists unique words in xml-files, where the bodies are 
-defined as questions (PostTypeId = 1)
+xmlmapper(infile)
+main mapper function, uses cleanBody()
+Outputs an integer of how many questions (PostTypeId = 1)
+have 10 or more words in their titles (including stopwords)
 
 input:
   string source           : xml-tag to extract from
@@ -25,13 +25,18 @@ returns:
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
+    count = 0
+
     # Iterates through each xml-row and extracts data
     for titles in parsed:
-        if (titles.attrib["PostTypeId"] == "1"):
+        if titles.attrib["PostTypeId"] == "1":
             title = titles.attrib[source]
 
             words = cleanBody(title)
-            mapper_core(words)
+
+            if len(words) >10 :
+                count += 1
+    
+    print (count)
 
 xmlmapper("Title")
-

### 2020-02-17 Code/task1/task1c/1cReducer.py

@@ -1,0 +1,24 @@
+#!/usr/bin/python3
+import sys
+
+"""
+reducer()
+main reducer function
+Outputs an integer of how many questions (PostTypeId = 1)
+have 10 or more words in their titles (including stopwords)
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():    
+    total_average = 0
+
+    for line in sys.stdin:
+        total_average += int(line.strip())
+    
+    print(total_average)
+
+reducer()

### 2020-02-17 Code/task1/task1c/run1c_windows.sh

@@ -1,15 +1,16 @@
 # Assumptions:
-# 1. the dataset in the cluster is located at "news"
+# 1. the dataset in the cluster is located under "Dataset/"
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-tasknumb=
-taskname=
+taskNumber = 1c
+taskName   = MoreThan10
+sourceFile = Posts
 
 #Simplify task change
-mapperfile=$tasknumb$taskname.py
-reducerfile="$tasknumb"reducer.py
-outfile=output$tasknumb
+mapperfile  = $taskNumber$taskName.py
+reducerfile = "$taskNumber"Reducer.py
+outfile     = output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile
@@ -19,12 +20,12 @@ apt-get install dos2unix
 dos2unix $mapperfile
 dos2unix $reducerfile
 
-#Main MapReduce function
+#Main MapReduce function call
 hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 -files $mapperfile,$reducerfile \
 -mapper $mapperfile \
 -reducer $reducerfile \
--input posts.xml \
+-input Dataset/$sourceFile.xml \
 -output $outfile
 
 #Read file and save it locally

### 2020-02-17 Code/task1/task1d/1dStopWords.py

@@ -1,6 +1,6 @@
 #!/usr/bin/python3
 import sys
-sys.path.append('../') #allows access functions in parallel folder
+sys.path.append('../../') #allows access functions in parallel folder
 import ProjectFunctions.functions as proj
 
 cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser

### 2020-02-17 Code/task1/task1d/run1d_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 1d
+taskName   = StopWords
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task1/task1e/1ePigTop10.py

@@ -6,10 +6,10 @@ import ProjectFunctions.functions as proj
 cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser
 
 """
-xmlmapper(source, infile=sys.stdin)
+xmlmapper(infile)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Combined with 1ePig.pig, lists top 10 words (not counting
+stopwords) found in titles
 
 input:
   string source           : xml-tag to extract from
@@ -22,16 +22,29 @@ input:
 returns:
   None, prints words into format acceptable by Hadoop
 """
+
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
     # Iterates through each xml-row and extracts data
-    for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+    for titles in parsed:
+        if (titles.attrib["PostTypeId"] == "1"):
+            title = titles.attrib[source]
 
-            words = cleanBody(body)
+            words = cleanBody(title)
+
+            for Stop in StopW:
+                if Stop in words:
+                    words.remove(Stop)
 
             mapper_core(words)
 
-xmlmapper("Text")
+
+# Extracts stopwords to a useable format
+with open("StopWords.txt","r") as StopWords:
+    StopW = StopWords.readlines()
+    StopW = [i[:-1] for i in StopW[:-1]] + [StopW[-1]]
+    for i in range(len(StopW)):
+        StopW[i] = StopW[i].replace("'","")
+
+xmlmapper("Title")

### 2020-02-17 Code/task1/task1e/1eReducer.py

@@ -1,0 +1,45 @@
+#!/usr/bin/python3
+import sys
+# using a dictionary to map words to their counts
+
+"""
+reducer()
+main reducer function
+Counts words in xml-files, where the bodies are defined as
+questions (PostTypeId = 1). Stopwords removed as defined in
+stopwords.txt, taken taken on 16.10.2019 from
+https://raw.githubusercontent.com/naimdjon/stopwords/master/stopwords.txt
+
+input:
+  string source           : xml-tag to extract from
+                            infile
+
+  string infile=sys.stdin : parsed xml-file
+                            if given a string, will look in
+                            working directory for xml to parse
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+
+def reducer():
+    current_word = None
+    current_count = 0
+    word = None
+
+    for line in sys.stdin:
+        line = line.strip()
+        word,count = line.split()
+
+        count = int(count)
+        if current_word ==word:
+            current_count += count
+        else:
+            if current_word:
+                print("%s %s "%(current_word, current_count))
+            current_word = word
+            current_count = count
+    if current_word== word:
+        print("%s %s "% (current_word, current_count))
+
+reducer()

### 2020-02-17 Code/task1/task1f/1fReducer.py

@@ -1,0 +1,33 @@
+#!/usr/bin/python3
+import sys
+
+"""
+reducer()
+main reducer function
+creates a dictionary over unique tags in an xml-file
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():
+    current_word = None
+    word = None
+
+    for line in sys.stdin:
+        line = line.strip()
+        word = line.split()[0]
+
+        if current_word ==word:
+            pass
+        else:
+            if current_word:
+                print("%s "%(current_word))
+            current_word = word
+ 
+    if current_word== word:
+        print("%s "% (current_word))
+
+reducer()

### 2020-02-17 Code/task1/task1f/1fTags.py

@@ -7,9 +7,7 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 
 """
 xmlmapper(source, infile=sys.stdin)
-main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+creates a dictionary over unique tags in an xml-file
 
 input:
   string source           : xml-tag to extract from
@@ -25,13 +23,18 @@ returns:
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
+    tag = None
     # Iterates through each xml-row and extracts data
-    for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+    for tags in parsed:
+        try:
+            tag = tags.attrib[source]  
+        except KeyError:
+            continue
 
-            words = cleanBody(body)
+        tag = tag.replace(">", " ")
+        tag = tag.replace("<", "")
+        words = cleanBody(tag)
 
-            mapper_core(words)
+        mapper_core(words)
 
-xmlmapper("Text")
+xmlmapper("Tags")

### 2020-02-17 Code/task1/task1f/run1f_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 1f
+taskName   = Tags
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task2/task2a/2aReducer.py

@@ -1,0 +1,23 @@
+#!/usr/bin/python3
+import sys
+
+"""
+reducer()
+main reducer function
+Counts how many unique users there is in an xml database
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():    
+    total_average = 0
+
+    for line in sys.stdin:
+        total_average += int(line.strip())
+    
+    print(total_average)
+
+reducer()

### 2020-02-17 Code/task2/task2b/2bUnique.py

@@ -3,13 +3,13 @@ import sys
 sys.path.append('../../') #allows access functions in parallel folder
 import ProjectFunctions.functions as proj
 
-cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser
+cleanBody, parser = proj.cleanBody, proj.xmlparser
 
 """
-xmlmapper(source, infile=sys.stdin)
+xmlmapper(infile)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Lists all unique users in an xml databse by unique Id
+and displayname
 
 input:
   string source           : xml-tag to extract from
@@ -26,12 +26,12 @@ def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
     # Iterates through each xml-row and extracts data
-    for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+    for user in parsed:
 
-            words = cleanBody(body)
+        userID   = user.attrib[source]
+        userName = user.attrib["DisplayName"]
 
-            mapper_core(words)
+        userName = " ".join(cleanBody(userName))
 
-xmlmapper("Text")
+        print(userID + "|" + userName)
+xmlmapper("Id")

### 2020-02-17 Code/task2/task2c/2cReducer.py

@@ -1,0 +1,35 @@
+#!/usr/bin/python3
+import sys
+
+"""
+reducer()
+main reducer function
+Lists top 10 users in terms of their reputation
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():
+    current_word = None
+    current_count = 0
+    word = None
+
+    for line in sys.stdin:
+        line = line.strip()
+        id,rep = line.split(" ")
+
+        rep = int(rep)
+        if current_word ==id:
+            current_count += rep
+        else:
+            if current_word:
+                print("%s %s "%(current_word, current_count))
+            current_word = id
+            current_count = rep
+    if current_word== id:
+        print("%s %s "% (current_word, current_count))
+
+reducer()

### 2020-02-17 Code/task2/task2c/2cTopMiners.py

@@ -6,10 +6,9 @@ import ProjectFunctions.functions as proj
 cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser
 
 """
-xmlmapper(source, infile=sys.stdin)
+xmlmapper(infile)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Lists top 10 users in terms of their reputation
 
 input:
   string source           : xml-tag to extract from
@@ -26,12 +25,13 @@ def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
     # Iterates through each xml-row and extracts data
-    for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+    for miner in parsed:
+        name = miner.attrib[source]
+        rep = int(miner.attrib["Reputation"])
+        words = " ".join(cleanBody(name))
 
-            words = cleanBody(body)
+        name = cleanBody(name)
 
-            mapper_core(words)
+        mapper_core([name, [rep]], "double")
 
-xmlmapper("Text")
+xmlmapper("DisplayName")

### 2020-02-17 Code/task2/task2d/2dTopQuestions.py

@@ -6,10 +6,9 @@ import ProjectFunctions.functions as proj
 cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser
 
 """
-xmlmapper(source, infile=sys.stdin)
+xmlmapper(infile)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Outputs top 10 questions in terms of their Score
 
 input:
   string source           : xml-tag to extract from
@@ -26,12 +25,14 @@ def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
     # Iterates through each xml-row and extracts data
-    for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+    for question in parsed:
+        if (question.attrib["PostTypeId"] == "1"):
+            id = question.attrib[source]
+            title = question.attrib["Title"]
+            score = question.attrib["Score"]
 
-            words = cleanBody(body)
+            words = cleanBody(title)
+            Title = " ".join(words)
+            mapper_core([[id],[score], [Title]], "triple")
 
-            mapper_core(words)
-
-xmlmapper("Text")
+xmlmapper("Id")

### 2020-02-17 Code/task2/task2d/run2d_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 2d
+taskName   = TopQiestions
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task2/task2e/2eFavoriteQuestion.py

@@ -6,10 +6,9 @@ import ProjectFunctions.functions as proj
 cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser
 
 """
-xmlmapper(source, infile=sys.stdin)
+xmlmapper(infile)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Outputs the top 10 questions in terms of their FavoriteCount
 
 input:
   string source           : xml-tag to extract from
@@ -26,12 +25,20 @@ def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
     # Iterates through each xml-row and extracts data
-    for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+    for question in parsed:
+        if (question.attrib["PostTypeId"] == "1"):
 
-            words = cleanBody(body)
+            try:
+                score = question.attrib["FavoriteCount"]
+            except KeyError:
+                continue
 
-            mapper_core(words)
+            id    = question.attrib[source]
+            title = question.attrib["Title"]
 
-xmlmapper("Text")
+            words = cleanBody(title)
+            Title = " ".join(words)
+
+            mapper_core([[id],[score], [Title]], "triple")
+
+xmlmapper("Id")

### 2020-02-17 Code/task2/task2e/run2e_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 2e
+taskName   = FacoriteQuestion
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task2/task2f/2fAverage.py

@@ -7,9 +7,8 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 
 """
 xmlmapper(source, infile=sys.stdin)
-main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+main mapper function, uses cleanBody()
+Outputs the average amount of answers per question
 
 input:
   string source           : xml-tag to extract from
@@ -25,13 +24,15 @@ returns:
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
+    total = 0
+    count = 0
     # Iterates through each xml-row and extracts data
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+        if (post.attrib["PostTypeId"] == "1"):
+            total += int(post.attrib[source])
+            count += 1
 
-            words = cleanBody(body)
+    average = total/count
+    print(average)
 
-            mapper_core(words)
-
-xmlmapper("Text")
+xmlmapper("AnswerCount")

### 2020-02-17 Code/task2/task2f/2fReducer.py

@@ -1,0 +1,24 @@
+#!/usr/bin/python3
+import sys
+
+"""
+reducer()
+main reducer function
+Outputs an integer of how many questions (PostTypeId = 1)
+have 10 or more words in their titles (including stopwords)
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():    
+    total_average = 0
+
+    for line in sys.stdin:
+        total_average += float(line.strip())
+    
+    print(total_average)
+
+reducer()

### 2020-02-17 Code/task2/task2g/2gCountries.py

@@ -7,9 +7,8 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 
 """
 xmlmapper(source, infile=sys.stdin)
-main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+main mapper function, uses cleanBody()
+Counts amount of users in a given location
 
 input:
   string source           : xml-tag to extract from
@@ -24,14 +23,18 @@ returns:
 """
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
-
+    
     # Iterates through each xml-row and extracts data
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+        try:
+            Location = post.attrib[source]
+        except KeyError:
+            continue
 
-            words = cleanBody(body)
+        Location = Location.split(",")[-1]
+            
+        loc = " ".join(cleanBody(Location))
 
-            mapper_core(words)
+        print(loc, "|", 1)
 
-xmlmapper("Text")
+xmlmapper("Location")

### 2020-02-17 Code/task2/task2h/2hName.py

@@ -7,9 +7,9 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 
 """
 xmlmapper(source, infile=sys.stdin)
-main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+main mapper function, uses cleanBody()
+Outputs top 10 popular usernames
+
 
 input:
   string source           : xml-tag to extract from
@@ -27,11 +27,13 @@ def xmlmapper(source, infile=sys.stdin):
 
     # Iterates through each xml-row and extracts data
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+        try:
+            Name = post.attrib[source]
+        except KeyError:
+            continue
 
-            words = cleanBody(body)
+        name = " ".join(cleanBody(Name))
+        print(name,"|",1)
 
-            mapper_core(words)
 
-xmlmapper("Text")
+xmlmapper("DisplayName")

### 2020-02-17 Code/task2/task2h/run2h_windows.sh

@@ -3,9 +3,9 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
-sourceFile = Posts
+taskNumber = 2h
+taskName   = Name
+sourceFile = Users
 
 #Simplify task change
 mapperfile  = $taskNumber$taskName.py

### 2020-02-17 Code/task2/task2i/2iAnswers.py

@@ -8,8 +8,7 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 """
 xmlmapper(source, infile=sys.stdin)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Outputs the number of questions that have at least 1 answer
 
 input:
   string source           : xml-tag to extract from
@@ -25,13 +24,15 @@ returns:
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
+    count = 0
+
     # Iterates through each xml-row and extracts data
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
-            body = post.attrib[source]
+        if (post.attrib["PostTypeId"] == "1" and\
+                int(post.attrib["AnswerCount"]) > 0):
 
-            words = cleanBody(body)
+            count += 1
 
-            mapper_core(words)
+    print("Answers %d"%(count))
 
-xmlmapper("Text")
+xmlmapper("AnswerCount")

### 2020-02-17 Code/task2/task2i/run2i_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 2i
+taskName   = Answers
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task3/task3a/3aBigram.py

@@ -8,7 +8,7 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 """
 xmlmapper(source, infile=sys.stdin)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
+Counts bigrams (list of tree words) in xml-files, where the bodies are defined as 
 questions (PostTypeId = 1)
 
 input:
@@ -27,11 +27,12 @@ def xmlmapper(source, infile=sys.stdin):
 
     # Iterates through each xml-row and extracts data
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
+        if (post.attrib["PostTypeId"] == "1"):
             body = post.attrib[source]
 
             words = cleanBody(body)
 
-            mapper_core(words)
+            for i in range(len(words)-1):
+                print("{} {} | 1".format(words[i], words[i+1]))
 
-xmlmapper("Text")
+xmlmapper("Title")

### 2020-02-17 Code/task3/task3a/run3a_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 3a
+taskName   = Bigram
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task3/task3b/3bReducer.py

@@ -1,0 +1,42 @@
+#!/usr/bin/python3
+import sys
+
+"""
+xmlmapper(source, infile=sys.stdin)
+main reducer function
+Counts trigrams in xml-files, where the bodies are defined as 
+questions (PostTypeId = 1)
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():
+    current_word = None
+    current_count = 0
+    word = None
+    
+    most_common = ["NOTABIGRAM", 0]
+
+    for line in sys.stdin:
+        line = line.strip()
+        word,count = line.split("|")
+
+        count = int(count)
+        if current_word ==word:
+            current_count += count
+        else:
+            if current_word:
+                if current_count > most_common[1]:
+                    most_common = [current_word, current_count]
+            current_word = word
+            current_count = count
+    if current_word== word:
+        if current_count > most_common[1]:
+            most_common = [current_word, current_count]
+
+    print(most_common[0],",", most_common[1])
+
+reducer()

### 2020-02-17 Code/task3/task3b/3bTrigram.py

@@ -7,9 +7,9 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 
 """
 xmlmapper(source, infile=sys.stdin)
-main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+main mapper function, uses cleanBody()
+Counts trigrams (list of tree words) in xml-files, 
+where the bodies are defined as questions (PostTypeId = 1)
 
 input:
   string source           : xml-tag to extract from
@@ -27,11 +27,13 @@ def xmlmapper(source, infile=sys.stdin):
 
     # Iterates through each xml-row and extracts data
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
+        if (post.attrib["PostTypeId"] == "1"):
             body = post.attrib[source]
 
             words = cleanBody(body)
 
-            mapper_core(words)
+            for i in range(len(words)-2):
+                print("{} {} {} | 1"\
+                .format(words[i], words[i+1], words[i+2]))
 
-xmlmapper("Text")
+xmlmapper("Title")

### 2020-02-17 Code/task3/task3b/run3b_windows.sh

@@ -3,8 +3,8 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
+taskNumber = 3b
+taskName   = Trigram
 sourceFile = Posts
 
 #Simplify task change

### 2020-02-17 Code/task3/task3c/3cCombiner.py

@@ -3,13 +3,13 @@ import sys
 sys.path.append('../../') #allows access functions in parallel folder
 import ProjectFunctions.functions as proj
 
-cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser
+cleanBody, parser = proj.cleanBody, proj.xmlparser
 
 """
 xmlmapper(source, infile=sys.stdin)
-main mapper function, uses cleanBody() and mapper_core()
+main mapper function, uses cleanBody()
 Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+questions (PostTypeId = 1). Uses a combiner
 
 input:
   string source           : xml-tag to extract from
@@ -25,13 +25,32 @@ returns:
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
+    allwords = {}
+
     # Iterates through each xml-row and extracts data
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
+        if (post.attrib["PostTypeId"] == "1"):
             body = post.attrib[source]
 
             words = cleanBody(body)
 
-            mapper_core(words)
+            #Combiner
+            for word in words:
+                if word == "":
+                    continue
+                if word in allwords:
+                    allwords[word]+= 1
+                else:
+                    allwords[word] = 1
 
-xmlmapper("Text")
+    #Converts allwords from dict to list
+    wordslist = []
+    for word in allwords:
+        wordslist.append([word, allwords[word]])
+
+    wordslist.sort(key=lambda x: x[-1])
+
+    for word, count in wordslist:
+        print("%s %d "%(word, count))
+
+xmlmapper("Body")

### 2020-02-17 Code/task3/task3c/3cReducer.py

@@ -1,0 +1,37 @@
+#!/usr/bin/python3
+import sys
+
+"""
+xmlmapper(source, infile=sys.stdin)
+main reducer function
+Counts words in xml-files, where the bodies are defined as
+questions (PostTypeId = 1). Uses a combiner
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():
+    current_word = None
+    current_count = 0
+    word = None
+    
+    for line in sys.stdin:
+        line = line.strip()
+        word,count = line.split()
+
+        count = int(count)
+        if current_word ==word:
+            current_count += count
+        else:
+            if current_word:
+                print("%s %s "%(current_word, current_count))
+            current_word = word
+            current_count = count
+            
+    if current_word== word:
+        print("%s %s "% (current_word, current_count))
+
+reducer()

### 2020-02-17 Code/task3/task3d/3dUseless.py

@@ -8,8 +8,7 @@ cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparse
 """
 xmlmapper(source, infile=sys.stdin)
 main mapper function, uses cleanBody() and mapper_core()
-Counts words in xml-files, where the bodies are defined as
-questions (PostTypeId = 1)
+Counts the amount of times the word useless is used
 
 input:
   string source           : xml-tag to extract from
@@ -25,13 +24,18 @@ returns:
 def xmlmapper(source, infile=sys.stdin):
     parsed = parser(infile)
 
-    # Iterates through each xml-row and extracts data
+    count = 0
+
+    #Extracting the relevant section from the file
     for post in parsed:
-        if (post.attrib["PostId"] == "1"):
+        if (post.attrib["PostTypeId"] == "1"):
             body = post.attrib[source]
 
             words = cleanBody(body)
 
-            mapper_core(words)
+            if("useless" in words):
+                count +=1
+                
+    print(count)
 
-xmlmapper("Text")
+xmlmapper("Body")

### 2020-02-17 Code/task4/4Reducer.py

@@ -1,0 +1,58 @@
+#!/usr/bin/python3
+import sys
+
+"""
+reducer()
+main reducer function
+Indexes all words in bodies of questions, titles and
+answers according to the post Id of the posts it 
+appears in
+
+input:
+  None
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def reducer():
+    current_word = None
+    current_id = 0
+    word = None
+    ids = []
+
+    for line in sys.stdin:
+        line = line.strip()
+
+        try:
+            word,id = line.split()
+            id = int(id)
+        except ValueError:
+            continue
+
+        #Only updates current_word if different from word
+        #Only appends id to index if different from current_id
+        if current_word == word and current_id == id:
+            pass
+        elif current_word == word and current_id != id:
+            if current_word and not id in ids:
+                ids.append(id)
+        else:
+            ids.append(id)
+            idprint = ""
+            for id in ids:
+                idprint += "," + str(id)
+            print("%s, %s"%(current_word, idprint))
+
+            current_word = word
+            ids = []
+
+    if current_word== word:
+        ids.append(id)
+        idprint = ""
+        for id in ids:
+            idprint += "," + str(id)
+        print("%s, %s"%(current_word, idprint[1:]))
+
+        current_word = word
+
+reducer()

### 2020-02-17 Code/task1/task1a/run1a_windows.sh
Lol

@@ -3,20 +3,20 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1a
-taskName   = WordCount
-sourceFile = Posts
+taskNumber=1a
+taskName=WordCount
+sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile
 
 #For Windows-compatibility
-apt-get install dos2unix
+apt-get install dos2unix#
 dos2unix $mapperfile
 dos2unix $reducerfile
 

### 2020-02-17 Code/task1/task1b/run1b_windows.sh

@@ -3,9 +3,9 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 1b
-taskName   = Unique
-sourceFile = Posts
+taskNumber=1b
+taskName=Unique
+sourceFile=Posts
 
 #Simplify task change
 mapperfile  = $taskNumber$taskName.py

### 2020-02-17 Code/ProjectFunctions/functions.py
un-deleted ProjectFunctions
ok shut up, it was an accident

@@ -1,0 +1,95 @@
+import xml.etree.ElementTree as ET
+import string
+import sys
+from re import sub
+
+#Defines characters to be ignored, 123?{/¤ etc.
+ignore_char = string.digits + string.punctuation
+
+
+
+"""
+cleanBody(body)
+Formats string for mapper function
+non-case sensitive, removes HTML- and ascii formatting, 
+treats anything separeted by blank space or / as separate 
+words. Mispellings, names, filenames, functionnames etc. 
+will be counted as separate words
+
+input:
+  string body : string to be formatted
+
+returns:
+  string body : formatted string
+"""
+def cleanBody(body):
+    body = body.lower()
+    body = ascii(body)
+    body = sub("<.+?>","",body)
+    body = body.replace("/", " ")
+    body = body.strip()
+
+    for i in ignore_char:
+        body = body.replace(i, "")
+
+    body = body.split(" ")
+
+    return body
+
+
+"""
+mapper_core(words, mode="single")
+maps list of words into format acceptable by Hadoop
+has three modes, defined by parameter mode="single":
+  single: 
+    iterates through word in words, prints (word, 1)
+  double:
+    Assumes words is two-length list, separates into in1, in2
+    iterates through word, count in zip(in1, in2), prints them
+  triple
+    assumes words is three-length list, separates into in1, in2, in3
+    iterates through id, score, title in zip(in1, in2, in3), prints them
+
+input:
+  list words : words wanted to be passed into Hadoop
+               if 
+
+returns:
+  None, prints words into format acceptable by Hadoop
+"""
+def mapper_core(words, mode="single"):
+    if mode == "single":
+        for word in words:
+            if word not in ["", " "]:
+              print("%s %s" %(word,1)) #Emit the word
+
+    elif mode == "double":
+        in1, in2 = words
+        for word, count in zip(in1,in2):
+            if word not in ["", " "]:
+                print("%s %s" %(word,count)) #emit the words
+
+    elif mode == "triple":
+        in1, in2,in3  = words
+        for id, score, title in zip(in1,in2,in3):
+            print("%s %s %s" %(id,score, title)) #emit the words
+
+
+"""
+xmlparser(infile):
+Our chosen method for interpreting our dataset. Takes up
+a larger amount of memory for larger filesizes, but is
+fast enough and small enough for application in this dataset
+
+input:  
+  infile : unparsed xml-file
+
+returns:
[…]

### 2020-02-17 Code/runBasis_windows.sh
Removed spaces in bash-scripts so they work
done for tasks 2 and 4

@@ -3,14 +3,14 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber =
-taskName   =
-sourceFile =
+taskNumber=
+taskName=
+sourceFile=
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile= $taskNumber$taskName.py
+reducerfile= "$taskNumber"Reducer.py
+outfile= output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2a/run2a_windows.sh

@@ -3,14 +3,14 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 2a
-taskName   = Counting
-sourceFile = Users
+taskNumber=2a
+taskName=Counting
+sourceFile=Users
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2c/run2c_windows.sh

@@ -3,14 +3,14 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 2c
-taskName   = TopMiners
-sourceFile = Users
+taskNumber=2c
+taskName=TopMiners
+sourceFile=Users
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2d/run2d_windows.sh

@@ -3,14 +3,14 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 2d
-taskName   = TopQiestions
-sourceFile = Posts
+taskNumber=2d
+taskName=TopQiestions
+sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2g/run2g_windows.sh

@@ -3,14 +3,14 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 2g 
-taskName   = Countries
-sourceFile = Users
+taskNumber=2g 
+taskName=Countries
+sourceFile=Users
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2i/run2i_windows.sh

@@ -3,14 +3,14 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 2i
-taskName   = Answers
-sourceFile = Posts
+taskNumber=2i
+taskName=Answers
+sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task4/run4_windows.sh

@@ -3,14 +3,14 @@
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-taskNumber = 4
-taskName   = Index
-sourceFile = Posts
+taskNumber=4
+taskName=Index
+sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task1/task1b/run1b_windows.sh
d

@@ -8,9 +8,9 @@ taskName=Unique
 sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task1/task1d/run1d_windows.sh

@@ -8,9 +8,9 @@ taskName=StopWords
 sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task1/task1e/run1e_windows.sh

@@ -8,9 +8,9 @@ taskName=PigTop10
 sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task1/task1a/run1a_windows.sh
lol

@@ -19,7 +19,7 @@ hadoop fs -rm -r $outfile
 apt-get install dos2unix#
 dos2unix $mapperfile
 dos2unix $reducerfile
-2
+
 #Main MapReduce function call
 hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 -files $mapperfile,$reducerfile \

### 2020-02-17 Code/runBasis_windows.sh
ok this time it's actually fixed, shut up
Spaces have been removed

@@ -8,9 +8,9 @@ taskName=
 sourceFile=
 
 #Simplify task change
-mapperfile= $taskNumber$taskName.py
-reducerfile= "$taskNumber"Reducer.py
-outfile= output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2b/run2b_windows.sh
endringer

@@ -5,7 +5,7 @@
 #Simplify task change further
 taskNumber=2b
 taskName=Unique
-sourceFile = Users
+sourceFile=Users
 
 #Simplify task change
 mapperfile=$taskNumber$taskName.py

### 2020-02-17 Code/task1/task1e/run1e_windows.sh
commit so I can pull down the other damned edits

@@ -8,9 +8,9 @@ taskName=PigTop10
 sourceFile=Posts
 
 #Simplify task change
-mapperfile=$taskNumber$taskName.py
-reducerfile="$taskNumber"Reducer.py
-outfile=output$taskNumber
+mapperfile  = $taskNumber$taskName.py
+reducerfile = "$taskNumber"Reducer.py
+outfile     = output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile
@@ -31,6 +31,9 @@ hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 #Read file and save it locally
 hadoop fs -cat $outfile/*
 hadoop fs -copyToLocal $outfile
+
+#Run Pig-script
+pig 1ePig.pig
 
 #Automatic cleanup
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task1/task1e/run1e_windows.sh
1e now functions as it should

@@ -8,9 +8,9 @@ taskName=PigTop10
 sourceFile=Posts
 
 #Simplify task change
-mapperfile  = $taskNumber$taskName.py
-reducerfile = "$taskNumber"Reducer.py
-outfile     = output$taskNumber
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile
@@ -34,6 +34,7 @@ hadoop fs -copyToLocal $outfile
 
 #Run Pig-script
 pig 1ePig.pig
+hadoop fs -copyToLocal 1ePig_Output output1e
 
 #Automatic cleanup
 hadoop fs -rm -r $outfile

### 2020-02-17 Article_Final/main.tex
outputs changes and files

@@
 Other examples are 2c using task=2c and taskname=TopMiners and xmlsource=users.
-\lstinputlisting[title=bash-script for a windows-based environment]{Code_Files/runBasis_windows.sh}
+\lstinputlisting[title=bash-script for a windows-based environment]{Code_output/runBasis_windows.sh}
 
@@
 
-\lstinputlisting[firstline=500, lastline=510, title=1a\_output]{output1a.txt}
+\lstinputlisting[firstline=500, lastline=510, title=1a\_output]{Code_output/output1a.txt}
 
@@
 \textbf{Notes/Reflection}: Here again the choices made building the cleanBody function affects the output.
-\lstinputlisting[firstline=500,lastline=510,title=1b\_output]{output1b.txt}
+\lstinputlisting[firstline=500, lastline=510, title=1b\_output]{Code_output/output1b.txt}
 
@@
 \textbf{Notes/Reflection}: This MapReduce job is simpler, the reducer is unnecessary outside an environment with clusters.
-\lstinputlisting[firstline=1,lastline=1,title=1c\_output]{output1c.txt}
+\lstinputlisting[firstline=1,lastline=1,title=1c\_output]{Code_output/output1c}
 
@@
 \textbf{Notes/Reflection}: Given how we built cleanBody, we chose to remove the apostrophes (') from the stopwords, turning words like "we're" to "were".
-\lstinputlisting[firstline=500,lastline=509,title=1d\_output]{output1d.txt}
+\lstinputlisting[firstline=500,lastline=509,title=1d\_output]{Code_output/output1d}
 
@@
 \textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an hdfs cluster as opposed to a local storage location.
-\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{output1e.txt}
+\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{Code_output/output1e}
 
@@
 Some of the posts lacked any tag attribute, so we elected to pass over those.
-\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{output1f.txt}
+\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{Code_output/output1f}
 
@@
 \textbf{Notes/Reflection}: We interpreted "unique user" as a user with a unique Id attribute.
-\lstinputlisting[firstline=1,lastline=1,title=2a\_output]{output2a.txt}
+\lstinputlisting[firstline=1,lastline=1,title=2a\_output]{Code_output/output2a}
 
@@
 Since usernames can contain spaces, we elected to instead use | as a separator in hadoop.
- \lstinputlisting[firstline=500,lastline=510,title=2b\_output]{output2b.txt}
+ \lstinputlisting[firstline=500,lastline=510,title=2b\_output]{Code_output/output2b}
 
@@
 \textbf{Notes/Reflection}: We elected here to use pig to order the MapReduce output in order to get experience.
-\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{output2c.txt}
+\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{Code_output/output2c}
 
@@
 \textbf{Notes/Reflection}: The reducer could potentially be improved by only keeping 10 elements in the list at once, changing them out as higher scores were encountered.
-\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{output2d.txt}
+\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{Code_output/output2d}
 
@@
 \textbf{Notes/Reflection}: Here, like 1f Tags, some posts had to be skipped due to their lacking any FavoriteCount-attribute.
-\lstinputlisting[firstline=1,lastline=10,title=2e\_output]{output2e.txt}
+\lstinputlisting[firstline=1,lastline=10,title=2e\_output]{Code_output/output2e}
 
@@
 \textbf{Notes/Reflection}: We have elected to not limit the amount of decimals.
-\lstinputlisting[firstline=1,lastline=10,title=2f\_output]{output2f.txt}
+\lstinputlisting[firstline=1,lastline=10,title=2f\_output]{Code_output/output2f}
 
@@
 Locations like "California, USA", "California, United States", and "US" will be interpreted as "usa", "united states", and "us", respectively.
-\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{output2g.txt}
+\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{Code_output/output2g}
 
@@
 Due to the nature of Displaynames usually not being full legal names, we have elected to interpret a "name" as the full name given in DisplayName.
-\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{output2h.txt}
+\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{Code_output/output2h}
 
@@
 \textbf{Implementation}: This mapper functions in the same way as 1c MoreThan10 except it checks whether AnswerCount is larger than or equal to 1 instead of whether the title word length is larger than 10.
-\lstinputlisting[firstline=1,lastline=10,title=2i\_output]{output2i.txt}
+\lstinputlisting[firstline=1,lastline=10,title=2i\_output]{Code_output/output2i}
 
@@
 \textbf{Notes/Reflection}: In the print-loop we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
-\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{output3a.txt}
+\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{Code_output/output3a}
 
@@
 \textbf{Notes/Reflection}: The mapper, as in 3a Bigram, limited the print-loop to range(len(words)-2) and printed words[i], words[i+1], and words[i+2].
-\lstinputlisting[firstline=1,lastline=10,title=3b\_output]{output3b.txt}
+\lstinputlisting[firstline=1,lastline=10,title=3b\_output]{Code_output/output3b}
 
@@
 This is less relevant in our case, working with relatively small datasets.
-\lstinputlisting[firstline=1,lastline=10,title=3c\_output]{output1a.txt}
+\lstinputlisting[firstline=1,lastline=10,title=3c\_output]{Code_output/output1a}
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=0.5\linewidth]{images/time.png}
+\caption{on the left side is the combiner, and right side is without the combiner. }
+\label{fig:figure_label}
+\end{figure}
 
@@
 \\ \\
-\lstinputlisting[firstline=1,lastline=10,title=3d\_output]{output3d.txt}
+\lstinputlisting[firstline=1,lastline=10,title=3d\_output]{Code_output/output3d}
 
@@
 \textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary, since we are working with small file-sizes.
-\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{output4a.txt}
+\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{Code_output/output4a}
 

### 2020-02-17 Code/task4/4Index.py

@@ -1,6 +1,6 @@
 #!/usr/bin/python3
 import sys
-sys.path.append('../../') #allows access functions in parallel folder
+sys.path.append('../') #allows access functions in parallel folder
 import ProjectFunctions.functions as proj
 
 cleanBody, mapper_core, parser = proj.cleanBody, proj.mapper_core, proj.xmlparser

### 2020-02-17 Code/task1/task1e/run1e_windows.sh
fixed pig-related 1e, 2c and 2d

@@ -33,8 +33,8 @@ hadoop fs -cat $outfile/*
 hadoop fs -copyToLocal $outfile
 
 #Run Pig-script
-pig 1ePig.pig
-hadoop fs -copyToLocal 1ePig_Output output1e
+pig "$taskNumber"Pig.pig
+hadoop fs -copyToLocal "$taskNumber"Pig_Output output$taskNumber
 
 #Automatic cleanup
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2c/run2c_windows.sh

@@ -32,5 +32,9 @@ hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 hadoop fs -cat $outfile/*
 hadoop fs -copyToLocal $outfile
 
+#Run Pig-script
+pig "$taskNumber"Pig.pig
+hadoop fs -copyToLocal "$taskNumber"Pig_Output output2c
+
 #Automatic cleanup
 hadoop fs -rm -r $outfile

### 2020-02-17 Code/task2/task2d/run2d_windows.sh

@@ -4,7 +4,7 @@
 
 #Simplify task change further
 taskNumber=2d
-taskName=TopQiestions
+taskName=TopQuestions
 sourceFile=Posts
 
 #Simplify task change
@@ -31,6 +31,10 @@ hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 #Read file and save it locally
 hadoop fs -cat $outfile/*
 hadoop fs -copyToLocal $outfile
+
+#Run Pig-script
+pig "$taskNumber"Pig.pig
+hadoop fs -copyToLocal "$taskNumber"Pig_Output output2c
 
 #Automatic cleanup
 hadoop fs -rm -r $outfile

### 2020-02-17 Article_Final/main.tex

@@
 The result should be a list containing the top 10 questions, showing id, question, and score.\\ \\
-\textbf{Implementation}: This mapper job functions similarly to 2c Top miners except it puts out 3 parsed attributes using the "triple"-mode of mapper\_core.
+\textbf{Implementation}: This mapper job functions similarly to 2c Top users except it puts out 3 parsed attributes using the "triple"-mode of mapper\_core.
 The reducer performs the reduction and ordering, finding the 10 highest score values.

### 2020-02-17 Article_Final/main.tex
changed all file ensings to .txt, LaTeX now compiles

@@
 \usepackage{sectsty}
+\usepackage{float}
 \renewcommand{\thesection}{\Roman{section}}
@@
 \textbf{Notes/Reflection}: This MapReduce job is simpler, the reducer is unnecessary outside an environment with clusters.
-\lstinputlisting[firstline=1,lastline=1,title=1c\_output]{Code_output/output1c}
+\lstinputlisting[firstline=1,lastline=1,title=1c\_output]{Code_output/output1c.txt}
 
@@
 \textbf{Notes/Reflection}: Given how we built cleanBody, we chose to remove the apostrophes (') from the stopwords, turning words like "we're" to "were".
-\lstinputlisting[firstline=500,lastline=509,title=1d\_output]{Code_output/output1d}
+\lstinputlisting[firstline=500,lastline=509,title=1d\_output]{Code_output/output1d.txt}
 
@@
 \textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an hdfs cluster as opposed to a local storage location.
-\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{Code_output/output1e}
+\lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{Code_output/output1e.txt}
 
@@
 Some of the posts lacked any tag attribute, so we elected to pass over those.
-\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{Code_output/output1f}
+\lstinputlisting[firstline=500,lastline=510,title=1f\_output]{Code_output/output1f.txt}
 
@@
 \textbf{Notes/Reflection}: We interpreted "unique user" as a user with a unique Id attribute.
-\lstinputlisting[firstline=1,lastline=1,title=2a\_output]{Code_output/output2a}
+\lstinputlisting[firstline=1,lastline=1,title=2a\_output]{Code_output/output2a.txt}
 
@@
 Since usernames can contain spaces, we elected to instead use | as a separator in hadoop.
- \lstinputlisting[firstline=500,lastline=510,title=2b\_output]{Code_output/output2b}
+ \lstinputlisting[firstline=500,lastline=510,title=2b\_output]{Code_output/output2b.txt}
 
@@
 \textbf{Notes/Reflection}: We elected here to use pig to order the MapReduce output in order to get experience.
-\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{Code_output/output2c}
+\lstinputlisting[firstline=1,lastline=10,title=2c\_output]{Code_output/output2c.txt}
 
@@
 \textbf{Notes/Reflection}: The reducer could potentially be improved by only keeping 10 elements in the list at once, changing them out as higher scores were encountered.
-\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{Code_output/output2d}
+\lstinputlisting[firstline=1,lastline=10,title=2d\_output]{Code_output/output2d.txt}
 
@@
 \textbf{Notes/Reflection}: Here, like 1f Tags, some posts had to be skipped due to their lacking any FavoriteCount-attribute.
-\lstinputlisting[firstline=1,lastline=10,title=2e\_output]{Code_output/output2e}
+\lstinputlisting[firstline=1,lastline=10,title=2e\_output]{Code_output/output2e.txt}
 
@@
 \textbf{Notes/Reflection}: We have elected to not limit the amount of decimals.
-\lstinputlisting[firstline=1,lastline=10,title=2f\_output]{Code_output/output2f}
+\lstinputlisting[firstline=1,lastline=10,title=2f\_output]{Code_output/output2f.txt}
 
@@
 Locations like "California, USA", "California, United States", and "US" will be interpreted as "usa", "united states", and "us", respectively.
-\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{Code_output/output2g}
+\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{Code_output/output2g.txt}
 
@@
 Due to the nature of Displaynames usually not being full legal names, we have elected to interpret a "name" as the full name given in DisplayName.
-\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{Code_output/output2h}
+\lstinputlisting[firstline=1,lastline=21,title=2h\_output]{Code_output/output2h.txt}
 
@@
 \textbf{Implementation}: This mapper functions in the same way as 1c MoreThan10 except it checks whether AnswerCount is larger than or equal to 1 instead of whether the title word length is larger than 10.
-\lstinputlisting[firstline=1,lastline=10,title=2i\_output]{Code_output/output2i}
+\lstinputlisting[firstline=1,lastline=10,title=2i\_output]{Code_output/output2i.txt}
 
@@
 \textbf{Notes/Reflection}: In the print-loop we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
-\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{Code_output/output3a}
+\lstinputlisting[firstline=1,lastline=10,title=3a\_output]{Code_output/output3a.txt}
 
@@
 \textbf{Notes/Reflection}: The mapper, as in 3a Bigram, limited the print-loop to range(len(words)-2) and printed words[i], words[i+1], and words[i+2].
-\lstinputlisting[firstline=1,lastline=10,title=3b\_output]{Code_output/output3b}
+\lstinputlisting[firstline=1,lastline=10,title=3b\_output]{Code_output/output3b.txt}
 
@@
 This is less relevant in our case, working with relatively small datasets.
-\lstinputlisting[firstline=1,lastline=10,title=3c\_output]{Code_output/output1a}
+\lstinputlisting[firstline=1,lastline=10,title=3c\_output]{Code_output/output3c.txt}
 
@@
 \\ \\
-\lstinputlisting[firstline=1,lastline=10,title=3d\_output]{Code_output/output3d}
+\lstinputlisting[firstline=1,lastline=10,title=3d\_output]{Code_output/output3d.txt}
 
@@
 \textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary, since we are working with small file-sizes.
-\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{Code_output/output4a}
+\lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{Code_output/output4.txt}
 

### 2020-02-18 Article_Final/main.tex
Correct version of main.tex

@@
     }
-\usepackage{hyperref}
+\usepackage{hyperref}x	
 \hypersetup{
@@
 This report is of a structure where each task is independent and separately reported, frequently referring to each other due to their similarity.
-Each contains our assumptions about what the task is asking for, implementation, and any notes/reflections if necessary, opting to add notes/reflection more than necessary rather than less than necessary.\\
+Each contains our assumptions about what the task is asking for, implementation, and any notes/reflections if necessary, opting to add notes/reflection more than necessary rather than less than necessary.
 
 We chose to work together because both of us have python background, choosing python as main programming language.
-We explored a Science Fiction \& Fantasy Q\&A StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/scifi.stackexchange.com.7z} (accessed 17.02.2020) through Hadoop and Pig.\\
+We explored a Science Fiction \& Fantasy Q\&A StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/scifi.stackexchange.com.7z} (accessed 17.02.2020) through Hadoop and Pig.
+
 Hadoop is used to store and process big data, it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs.
@@
 Being oriented towards use in HTML, i.e.
-a website, the attributes contain ascii characters, punctuation, numbers and HTML tags that we don't want to be there.
+a website, the attributes contain ASCII characters, punctuation, numbers and HTML tags that we don't want to be there.
 For this we designed the function cleanBody, meant to clean the text gained from the XML-documents.
-Additionally a function to parse the XML files was required, for which we created XmlParser.
+Additionally a function to parse the XML files was required, for which we created xmlparser.
 Lastly, we created a general function that would perform the duties of putting out the results of the mapper function; mapper\_core.
 This section explains their implementations, details the modules imported and describes the bash-script used to run our python-scripts:
-
-\subsection{cleanBody}
+\subsection{\emph{cleanBody}}
 The cleanBody function formats strings to be parseable by python interpreters.
@@
 For instances the name "Jens-Petter" will be interpreted as the word "jenspetter" and the filepath /documents/folder/file.extension will be interpreted as the words "documents", "folder" and "fileextension".
-\\
 The function takes a string as input, formats it and outputs a list of all the words split by the string.split(" ") function.
-It uses the sub-function of the open source re module to remove HTML-tags and ascii function that is inherent starting with in python 3 to convert all characters to parse-able ascii text.
+It uses the sub-function of the open source re module to remove HTML-tags and ASCII function that is inherent starting with in Python 3 to convert all characters to parse-able ASCII text.
 The symbols in ignore\_char, which are characters we are not considering is defined by the builtin string functions string.punctuation and string.digits.
@@
 
-\subsection{XML Parser}
+\subsection{\emph{XML Parser}}
 The XML Parser function parses an xml using the open-source xml.etree.ElementTree.
@@
 
-\subsection{Import sys}
+\subsection{\emph{Import sys}}
 The sys module is an open-source, built in python function that allows us to add to the module search path with sys.path.append(\'../\'), enabling finding ProjectFunctions in a parallel folder, and read in the input for our mapper function and reduce function using sys.stdin.
@@
 
-\subsection{Import xml.etree.ElementTree}
+\subsection{\emph{Import xml.etree.ElementTree}}
 ElementTree is a part of the xml open-source library.
@@
 
-\subsection{Import re.sub}
+\subsection{\emph{Import re.sub}}
 re.sub is an open-source module we use in cleanBody to remove HTML-tags by removing anything that appears between two chevrons.
@@
 
-\subsection{Bash-script}
+\subsection{\emph{Bash-script}}
 As an example of files being run, this bash-script that was used while testing out scripts is provided.
@@
 It automatically names, cleans, and saves outputs locally.
-In this example task 4 index is being run.
-Other examples are 2c using task=2c and taskname=TopMiners and xmlsource=users.
-\lstinputlisting[title=bash-script for a windows-based environment]{Code_output/runBasis_windows.sh}
+Below is the base bash-script used for the tasks.
+The three variables taskNumber, taskName and sourceFile are used to operate it.
+The bash-scripts for the tasks containing Pig-scripts have an additional clause for the purpose of running the Pig-script.
+\lstinputlisting[title=Bash-script for a windows-based environment]{Code_output/runBasis_windows.sh}
+
+\subsection{\emph{Data trimming}}
+We use the environment Docker to act as a data cluster.
+Files that are bigger than 128MB  are not readable by the module we use to parse XMLs within the Docker environment (whether this is due to this being the standard size of a datablock we were not able to tell).
+Between the choice of running our software outside Docker and trimming the files for data, we elected to trim the relevant file for this case: Posts.xml.
+We deleted lines 74 699 through 171 247 and used the remaining data as a basis for out analysis.
 
 % --TASK1--
-\section{Task 1 Warmup}
+\section{Task 1 \emph{Warmup}}
 %This part of the task is about get to know how hadoop- and pig apache works and how to parse XML  files throught python code. 
-\subsection{WordCount}
+\subsection{\emph{WordCount}}
 \textbf{Assumption}: Count the words in body of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
@@
 \textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things as words that clearly are not.
-See line 7 in 1a\_output for examples; what is possibly a<br>, an html line break element, is interpreted as the word abr.
-\\ \\
+See line 2 in 1a\_output for example; what is possibly an "accordingly" followed by three lineskips and then an "in" is interpreted as "accordinglynnnin" and is counted as a word.
+\\
 
@@
 
-\subsection{Unique words}
+\subsection{\emph{Unique words}}
 \textbf{Assumption}: Write a MapReduce job which outputs unique words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
@@
 
-\subsection{MoreThan10}
+\subsection{\emph{MoreThan10}}
 \textbf{Assumption}: Write a simple python script to check the amount of words in titles of posts in \textit{Posts.xml}. The result should be a count of how many titles have more than 10 words. \\ \\
@@
 
-\subsection{Stopwords}
+\subsection{\emph{Stopwords}}
 \textbf{Assumption}: Write a simple python script based on task 1a to exclude \href{https://raw.githubusercontent.com/naimdjon/stopwords/master/stopwords.txt}{stopwords}: from body of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
@@
 
-\subsection{Pig top 10}
+\subsection{\emph{Pig top 10}}
 \textbf{Assumption}: Write a pig script to select top 10 listed words after removing the stopwords from \textit{Posts.xml}.
@@
 
-\subsection{Tags}
+\subsection{\emph{Tags}}
 \textbf{Assumption}: Write a MapReduce job to create a dictionary over unique tags in \textit{Posts.xml}. The result should be a list of unique tags.\\ \\
@@
 % --TASK2--
-\section{Task 2 Discover}
+\section{Task 2 \emph{Discover}}
 %This part of the task is about to looking through several
 
-\subsection{Counting}
+\subsection{\emph{Counting}}
 \textbf{Assumption}: Write a MapReduce job to count the total unique users there are in \textit{Users.xml}. The result should be a count of how many unique users there are.\\ \\
@@
 
-\subsection{Unique users}
+\subsection{\emph{Unique users}}
 \textbf{Assumption}: Write a MapReduce job based on 2a Counting to list the unique users in \textit{Users.xml}. The result should be a list containing unique users in the dataset. \\ \\
@@
 
-\subsection{Top miners}
+\subsection{\emph{Top users}}
 \textbf{Assumption}:Write a pig script or MapReduce job to find top 10 users based on Reputation attribute in \textit{Users.xml}.
@@
 
-\subsection{Top questions}
+\subsection{\emph{Top questions}}
 \textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on the Score attribute.
@@
 
-\subsection{Favorite questions}
+\subsection{\emph{Favorite questions}}
 \textbf{Assumption}: Write a pig script or MapReduce job to find top 10 title questions, identified by PostTypeID="1", in \textit{Posts.xml} based on FavouriteCount attribute.
@@
 
-\subsection{Average answers}
+\subsection{\emph{Average answers}}
 \textbf{Assumption}: Write a MapReduce job that calculates the average number of answers per question. The result should be a calculated average of all AnswerCount attributes. \\ \\
@@
 
-\subsection{Countries}
+\subsection{\emph{Countries}}
 \textbf{Assumption}: Write a MapReduce job to count the amount of users attributed to a country by the Location attribute in \textit{Users.xml}.
@@
 
-\subsection{Names}
+\subsection{\emph{Names}}
 \textbf{Assumption}: Write a pig script or MapReduce job to find the 10 most popular names in \textit{Users.xml}. The result should be a list top 10 common names. \\ \\
@@
 
-\subsection{Answers}
+\subsection{\emph{Answers}}
 \textbf{Assumption}: Write a python script to find how many questions, identified by PostTypeID="1", in \textit{Posts.xml} have at least one answer based on attribute AnswerCount.
@@
 % --TASK3--
-\section{Task 3 Numbers}
+\section{Task 3 \emph{Numbers}}
 
-\subsection{Bigram}
+\subsection{\emph{Bigram}}
 \textbf{Assumption}: We chose to write a MapReduce job to find the most common pair of adjacent words in the titles of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
@@
 
-\subsection{Trigram}
+\subsection{\emph{Trigram}}
 \textbf{Assumption}: Perform the same task as in 3a Bigram, except operate with trigrams (sequences of 3 words as opposed to 2). The result should be the most common trigram. \\ \\
@@
 
-\subsection{Combiner}
+\subsection{\emph{Combiner}}
 \textbf{Assumption}: Perform the same task as in 1a WordCount, except add a combiner before the mapper sends information to the reducer.
@@
 \textbf{Implementation} The MapReduce function is the same as in 1a WordCount, with a combiner ahead of the print function in the mapper. \\ \\
-\textbf{Notes/Reflection}: Having a combiner in a MapReduce job saves bandwidth and computational strain by decreasing the volume of data sent from the mapper.
-This is less relevant in our case, working with relatively small datasets.
+\textbf{Notes/Reflection}: Having a combiner in a MapReduce job saves bandwidth and computational strain by decreasing the volume of data sent from the mapper, as shown in \ref{fig:figure_label}.
 \lstinputlisting[firstline=1,lastline=10,title=3c\_output]{Code_output/output3c.txt}
@@
 \centering
-\includegraphics[width=0.5\linewidth]{images/time.png}
-\caption{on the left side is the combiner, and right side is without the combiner. }
+\includegraphics[width=1\linewidth]{images/time.png}
+\caption{TIming for our two methods, Leftmost shows 3c combiner, rightmost shows 1a WordCount}
 \label{fig:figure_label}
@@
 
-\subsection{Useless}
+\subsection{\emph{Useless}}
 \textbf{Assumption}: Write a MapReduce job to find how many times the word "useless" in occurs in the bodies of questions, identified by PostTypeID="1", in \textit{Posts.xml}.
@@
 % --TASK4--
-\section{Task 4 Search engine}
-\subsection{Title index}
+\section{Task 4 \emph{Search engine}}
+\subsection{\emph{Title index}}
 \textbf{Assumption}: Write MapReduce job to create index over titles, bodies and answers of questions in \textit{Posts.xml}.

### 2020-02-18 Article_Final/main.tex
s

@@
   }
-\usepackage{hyperref}x	
+\usepackage{hyperref}	
 \hypersetup{
@@
 \begin{abstract}
-In this assignment we parsed a dataset, in the form of XMLs, through a Hadoop- and pig apache.
-We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from science fiction and Fantasy stack exchange.
+In this assignment, we parsed through datasets, in the form of XMLs, through a Hadoop- and pig apache.
+We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from Science Fiction and Fantasy Q/A stack exchange.
 
@@
 
-We chose to work together because both of us have python background, choosing python as main programming language.
+We chose to work together because both of us have python background, choosing python as the main programming language.
 We explored a Science Fiction \& Fantasy Q\&A StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/scifi.stackexchange.com.7z} (accessed 17.02.2020) through Hadoop and Pig.
@@
 Hadoop is used to store and process big data, it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs.
-Hadoop provides a framework which allow users to write and test distributed systems and does not rely on hardware to provide fault tolerance, making it less apt for our small-scale applications, yet we use it for the experience.
+Hadoop provides a framework that allows users to write and test distributed systems and does not rely on hardware to provide fault tolerance, making it less apt for our small-scale applications, yet we use it for the experience.
 Pig is a MapReduce abstraction, working on Hadoop methods, that we use in some tasks due to its efficiency.
-We have elected to use both pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both show our ability to employ both methods and get experience with the two methods.
+We have elected to use both pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both shows our ability to employ both methods and get experience with the two methods.
 
 \section{Main functions}
-The datasets consists only XML files which, being of a document-oriented database, is structured into attributes attributed to each element of the file.
+The datasets consist only XML files which, being of a document-oriented database, is structured into attributes attributed to each element of the file.
 Being oriented towards use in HTML, i.e.
 a website, the attributes contain ASCII characters, punctuation, numbers and HTML tags that we don't want to be there.
-For this we designed the function cleanBody, meant to clean the text gained from the XML-documents.
-Additionally a function to parse the XML files was required, for which we created xmlparser.
+For this, we designed the function cleanBody, meant to clean the text gained from the XML-documents.
+Additionally, a function to parse the XML files was required, for which we created xmlparser.
 Lastly, we created a general function that would perform the duties of putting out the results of the mapper function; mapper\_core.
@@
 The cleanBody function formats strings to be parseable by python interpreters.
-The function removes case sensitivity, ascii characters, HTML formatting, and treats anything separated by blanked space or / as separated words.
+The function removes case sensitivity, ASCII characters, HTML formatting, and treats anything separated by blanked space or / as separated words.
 This simple implementation of text formatting will affect the results of some tasks.
-For instances the name "Jens-Petter" will be interpreted as the word "jenspetter" and the filepath /documents/folder/file.extension will be interpreted as the words "documents", "folder" and "fileextension".
+For instance, the name "Jens-Petter" will be interpreted as the word "jenspetter" and the file path /documents/folder/file.extension will be interpreted as the words "documents", "folder" and "fileextension".
 The function takes a string as input, formats it and outputs a list of all the words split by the string.split(" ") function.
@@
  \item Single: Assumes input "words" is a list of words to print. Prints word in words as (word, 1). Ignores empty strings and spaces.
-  \item Double: Assumes input "words" is two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
+ \item Double: Assumes input "words" are two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
  \item Triple: Assumes input "words" is three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
@@
 \subsection{\emph{XML Parser}}
-The XML Parser function parses an xml using the open-source xml.etree.ElementTree.
-For normal use it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
+The XML Parser function parses an XML using the open-source xml.etree.ElementTree.
+For normal use, it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
 Although parsing an entire XML-file takes up significant memory, this method fits our dataset.
 It has been separated out as a function so it may be easily replaced by other methods more fit for large files.
-The input for this function is a XML-file and the output is a parsed XML-file.
+The input for this function is an XML-file and the output is a parsed XML-file.
 
@@
 \subsection{\emph{Import xml.etree.ElementTree}}
-ElementTree is a part of the xml open-source library.
+ElementTree is a part of the XML open-source library.
 XML is an inherently hierarchical data format, being document-oriented, and is naturally represented using a tree-like structure.
@@
 As an example of files being run, this bash-script that was used while testing out scripts is provided.
-It was used on a windows PC, meaning scripts had to be converted to unix code.
-It automatically names, cleans, and saves outputs locally.
+It was used on a Windows PC, meaning scripts had to be converted to Unix code.
+It automatically names, cleans and saves outputs locally.
 Below is the base bash-script used for the tasks.
-The three variables taskNumber, taskName and sourceFile are used to operate it.
-The bash-scripts for the tasks containing Pig-scripts have an additional clause for the purpose of running the Pig-script.
+The three variables taskNumber, taskName, and sourceFile are used to operate it.
+The bash-scripts for the tasks containing Pig-scripts have an additional clause for running the Pig-script.
 \lstinputlisting[title=Bash-script for a windows-based environment]{Code_output/runBasis_windows.sh}
@@
 \subsection{\emph{Data trimming}}
-We use the environment Docker to act as a data cluster.
-Files that are bigger than 128MB  are not readable by the module we use to parse XMLs within the Docker environment (whether this is due to this being the standard size of a datablock we were not able to tell).
+We use the environment Docker, to act as a data cluster.
+Files that are bigger than 128MB are not readable by the module we use to parse XMLs within the Docker environment (whether this is due to this being the standard size of a data block we were not able to tell).
 Between the choice of running our software outside Docker and trimming the files for data, we elected to trim the relevant file for this case: Posts.xml.
-We deleted lines 74 699 through 171 247 and used the remaining data as a basis for out analysis.
+We deleted lines 74 699 through 171 247 and used the remaining data as a basis for our analysis.
 
@@
 \section{Task 1 \emph{Warmup}}
-%This part of the task is about get to know how hadoop- and pig apache works and how to parse XML  files throught python code. 
+%This part of the task is about to get to know how Hadoop- and Pig apache works and how to parse XML files through python code. 
 \subsection{\emph{WordCount}}
@@
 \\ \\
-\textbf{Implementation}: The mapper uses the xmlparser function to parse an XML-file, iterates through all rows in parsed file, cleans text using the cleanBody function and prints output for the reducer script by using the mapper\_core function.
+\textbf{Implementation}: The mapper uses the xmlparser function to parse an XML-file, iterates through all rows in the parsed file, cleans text using the cleanBody function and prints output for the reducer script by using the mapper\_core function.
 The reducer receives the mapper output, parses it and iterates through the parsed lines.
@@
 \\ \\
-\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things as words that clearly are not.
-See line 2 in 1a\_output for example; what is possibly an "accordingly" followed by three lineskips and then an "in" is interpreted as "accordinglynnnin" and is counted as a word.
+\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things like words that are not.
+See line 2 in 1a\_output for example; what is possibly an "accordingly" followed by three line skips and then an "in" is interpreted as "accordinglynnnin" and is counted as a word.
 \\
@@
 \subsection{\emph{Pig top 10}}
-\textbf{Assumption}: Write a pig script to select top 10 listed words after removing the stopwords from \textit{Posts.xml}.
+\textbf{Assumption}: Write a pig script to select the top 10 listed words after removing the stopwords from \textit{Posts.xml}.
 The output should be a list of the top 10 listed words and the corresponding occurrence count.\\ \\
@@
 \\ \\
-\textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an hdfs cluster as opposed to a local storage location.
+\textbf{Notes/Reflection}: We chose for this pig script to load its dataset from an HDFS cluster as opposed to a local storage location.
 \lstinputlisting[firstline=1,lastline=10,title=1ePig\_output]{Code_output/output1e.txt}
@@
 \\ \\
-\textbf{Notes/Reflection}: The tags are separated by chevrons, and would be fused by cleanBody, so we elected to replace them with spaces.
+\textbf{Notes/Reflection}: The tags are separated by chevrons and would be fused by cleanBody, so we elected to replace them with spaces.
 Some of the posts lacked any tag attribute, so we elected to pass over those.
@@
 \subsection{\emph{Top users}}
-\textbf{Assumption}:Write a pig script or MapReduce job to find top 10 users based on Reputation attribute in \textit{Users.xml}.
-The result should be a list of the 10 users based with the highest reputation value.
+\textbf{Assumption}: Write a pig script or MapReduce job to find the top 10 users based on the Reputation attribute in \textit{Users.xml}.
+The result should be a list of the 10 users based on the highest reputation value.
 \\ \\
-\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out name and id, it puts out name and the reputation attribute.
-Here, reputation is given to mapper\_core as a one-element list (mapper\_core called with arguments (name, [reputation])) due to it looping through its inputs.
+\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out name and id, it puts out a name and the reputation attribute.
+Here, reputation is given to mapper\_core as a one-element list (mapper\_core called with arguments (name, [reputation])) due to its looping through its inputs.
 The reducer is the same as the reducer of 2b Unique users.
 The pig script functions the same way as in 1e Pig Top 10\\ \\
-\textbf{Notes/Reflection}: We elected here to use pig to order the MapReduce output in order to get experience.
+\textbf{Notes/Reflection}: We elected here to use Pig-script to order the MapReduce output to get experience.
 \lstinputlisting[firstline=1,lastline=10,title=2c\_output]{Code_output/output2c.txt}
@@
 \\ \\
-\textbf{Implementation}: This mapper functions similarly to 1f tags, except instead of cleaning the tags, it uses "|" as a separator, since spaces are part of location.
+\textbf{Implementation}: This mapper functions similarly to 1f tags, except instead of cleaning the tags, it uses "|" as a separator since spaces are part of the location.
 If Location is separated by a \',\' the last part is treated as the country.
 \\ \\
-\textbf{Notes/Reflection}: Because by our judgement locations are typed in by users, we have elected to separate the country out of Location very simply by using \',\' as a separator.
+\textbf{Notes/Reflection}: Because by our judgment locations are typed in by users, we have elected to separate the country out of Location very simply by using \',\' as a separator.
 Anything after the last \',\' is treated as a country.
@@
 \subsection{\emph{Names}}
-\textbf{Assumption}: Write a pig script or MapReduce job to find the 10 most popular names in \textit{Users.xml}. The result should be a list top 10 common names. \\ \\
+\textbf{Assumption}: Write a pig script or MapReduce job to find the 10 most popular names in \textit{Users.xml}. The result should be a list of top 10 common names. \\ \\
 \textbf{Implementation}: This mapper functions similarly to 2g Countries, except it extracts the DisplayName-attribute in place of the Location-attribute.
@@
 \textbf{Notes/Reflection}: Here the most common name is User.
-This is due to our choice of removing numbers in cleanBody, combining User1, User2, User3 etc.
+This is due to our choice of removing numbers in cleanBody, combining User1, User2, User3, etc.
 The task suggested explicitly that we should split up names by spaces, perhaps wanting to separate out last names from first names.
@@
 \\ \\
-\textbf{Implementation}: This MapReduce is exactly the same as 1a WordCount, except we output each bigram in the body instead of each word.
+\textbf{Implementation}: This MapReduce is the same as 1a WordCount, except we output each bigram in the body instead of each word.
 Because of this we he had to forego the mapper\_core for a print function inside a loop looping through every bigram.
@@
 \\ \\
-\textbf{Notes/Reflection}: In the print-loop we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
+\textbf{Notes/Reflection}: In the print-loop, we had to limit the loop to i in range(len(words)-1), since we printed both words[i] and words[i+1], and doing otherwise would result in and out of range error.
 \lstinputlisting[firstline=1,lastline=10,title=3a\_output]{Code_output/output3a.txt}
@@
 \subsection{\emph{Title index}}
-\textbf{Assumption}: Write MapReduce job to create index over titles, bodies and answers of questions in \textit{Posts.xml}.
+\textbf{Assumption}: Write MapReduce job to create an index over titles, bodies, and answers of questions in \textit{Posts.xml}.
 The result should be a simple index that lists posts words appear in by their Id's.
@@
 It then forks over whether PostTypeId is 1 or 2, i.e.
-whether it is an answer or question, extracting the relevant id, body and title from the row.
+whether it is an answer or question, extracting the relevant id, body, and title from the row.
 It contains a combiner to speed up the process, removing duplicates.
@@
 \\ \\
-\textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary, since we are working with small file-sizes.
+\textbf{Notes/Reflection}: We elected to have a combiner in the mapper although it is not strictly necessary since we are working with small file-sizes.
 \lstinputlisting[firstline=1792,lastline=1800, title=4a\_output]{Code_output/output4.txt}
@@
 \section{Conclusion}
-Through this assignment we gained experience in using MapReduce jobs and pig scripts.
-We parsed XML-documents and extracted specific information we were looking for to be formatted to an output to each tasks.
+Through this assignment, we gained experience in using MapReduce jobs and pig scripts.
+We parsed XML-documents and extracted specific information we were looking for to be formatted to output to each task.
 

### 2020-02-18 Article_Final/main.tex
Article updated for grammar

@@
 \begin{abstract}
-In this assignment, we parsed through datasets, in the form of XMLs, through a Hadoop- and pig apache.
+In this assignment, we parsed through XML-based datasets using a Hadoop- and Pig Apache.
 We learned how to write MapReduce jobs and Pig scripts, and how effective it is on our dataset based on XML files from Science Fiction and Fantasy Q/A stack exchange.
@@
 	assignment_title = \par{Exploring Science Fiction and Fantasy}, % Title of your assignment
-	course_code   	 = \par{Fill in}, % Course code (ex. MA110)
+	course_code   	 = \par{MA140}, % Course code (ex. MA110)
 	course_name      = \par{Big Data}, % Course name (ex. Systems Development)
-	due_date		 = \par{24. February}, % Due date
+	due_date	    	 = \par{24th Feb 2020}, % Due date
 	student_name     = \par{-}, % Your name (or names, if group – separate names with ; semicolon)
@@
 This report is of a structure where each task is independent and separately reported, frequently referring to each other due to their similarity.
-Each contains our assumptions about what the task is asking for, implementation, and any notes/reflections if necessary, opting to add notes/reflection more than necessary rather than less than necessary.
+Each contains our assumptions about what the task is asking for, implementation, and any notes/reflections if necessary, opting to add notes/reflection more than necessary rather than less.
 
-We chose to work together because both of us have python background, choosing python as the main programming language.
+We chose to work together because we both have python background, choosing python as the main programming language.
 We explored a Science Fiction \& Fantasy Q\&A StackExchange dataset based in XML-files as given from \url{archive.org/download/stackexchange/scifi.stackexchange.com.7z} (accessed 17.02.2020) through Hadoop and Pig.
 
-Hadoop is used to store and process big data, it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs.
+Hadoop is used to store and process big amounts of data (Bit Data), it has enormous processing power potential and has the ability to handle virtually any number of tasks and jobs.
 Hadoop provides a framework that allows users to write and test distributed systems and does not rely on hardware to provide fault tolerance, making it less apt for our small-scale applications, yet we use it for the experience.
 Pig is a MapReduce abstraction, working on Hadoop methods, that we use in some tasks due to its efficiency.
-We have elected to use both pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both shows our ability to employ both methods and get experience with the two methods.
+We have elected to use both Pig-scripts and pure MapReduce for very similar tasks (see 2c and 2d) to both show our ability to employ both methods and get experience with the two methods.
 
@@
 a website, the attributes contain ASCII characters, punctuation, numbers and HTML tags that we don't want to be there.
-For this, we designed the function cleanBody, meant to clean the text gained from the XML-documents.
+For this, we designed the function cleanBody, meant to clean the text extracted from the XML-documents.
 Additionally, a function to parse the XML files was required, for which we created xmlparser.
@@
  \item Single: Assumes input "words" is a list of words to print. Prints word in words as (word, 1). Ignores empty strings and spaces.
- \item Double: Assumes input "words" are two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
- \item Triple: Assumes input "words" is three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
+ \item Double: Assumes input "words" is comprised of two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
+ \item Triple: Assumes input "words" is comprised of three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
 \end{itemize}
@@
   elif mode == "triple":
-    in1, in2,in3 = words
+    in1, in2, in3 = words
     for id, score, title in zip(in1,in2,in3):
@@
 The XML Parser function parses an XML using the open-source xml.etree.ElementTree.
-For normal use, it uses sys.stdin as input, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
-Although parsing an entire XML-file takes up significant memory, this method fits our dataset.
-It has been separated out as a function so it may be easily replaced by other methods more fit for large files.
-The input for this function is an XML-file and the output is a parsed XML-file.
+It uses sys.stdin as input for normal, Hadoop-based use, but for debugging purposes it also contains a clause that lets it accept a string (see the isinstance(infile, str) check) as a path to the location of an XML-file.\\
+Parsing an entire XML-file takes up a significant amount of memory, so we separated it out as an imported function.
+This makes it simple to exchange it with another method that could more easily deal with larger files.
 
@@
 \\ \\
-\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things like words that are not.
+\textbf{Notes/Reflection}: Here the choices made building the cleanBody function affects the output, interpreting some things as words that are not.
 See line 2 in 1a\_output for example; what is possibly an "accordingly" followed by three line skips and then an "in" is interpreted as "accordinglynnnin" and is counted as a word.
@@
 \\ \\
-\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out name and id, it puts out a name and the reputation attribute.
+\textbf{Implementation}: This mapper job is based on 2b Unique users, except instead of putting out a name and its corresponding id, it puts out a name and its corresponding reputation attribute.
 Here, reputation is given to mapper\_core as a one-element list (mapper\_core called with arguments (name, [reputation])) due to its looping through its inputs.
@@
 Through this assignment, we gained experience in using MapReduce jobs and pig scripts.
-We parsed XML-documents and extracted specific information we were looking for to be formatted to output to each task.
+We parsed XML-documents and extracted specific information we were looking for to be formatted to an output for each task.
 

### 2020-02-18 Article_Final/Code_output/runBasis_windows.sh
Big D energy :)

@@ -1,15 +1,16 @@
 # Assumptions:
-# 1. the dataset in the cluster is located at "news"
+# 1. the dataset in the cluster is located under "Dataset/"
 # 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
 
 #Simplify task change further
-tasknumb=
-taskname=
+taskNumber=
+taskName=
+sourceFile=
 
 #Simplify task change
-mapperfile=$tasknumb$taskname.py
-reducerfile="$tasknumb"reducer.py
-outfile=output$tasknumb
+mapperfile=$taskNumber$taskName.py
+reducerfile="$taskNumber"Reducer.py
+outfile=output$taskNumber
 
 #Automatic removal
 hadoop fs -rm -r $outfile
@@ -19,12 +20,12 @@ apt-get install dos2unix
 dos2unix $mapperfile
 dos2unix $reducerfile
 
-#Main MapReduce function
+#Main MapReduce function call
 hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
 -files $mapperfile,$reducerfile \
 -mapper $mapperfile \
 -reducer $reducerfile \
--input posts.xml \
+-input Dataset/$sourceFile.xml \
 -output $outfile
 
 #Read file and save it locally

### 2020-02-18 Article_Final/runBasis_windows.sh

@@ -1,35 +1,0 @@
-# Assumptions:
-# 1. the dataset in the cluster is located at "news"
-# 2. the current directory contains files mapper.py and reducer.py for mapper and reducer code respectively
-
-#Simplify task change further
-tasknumb=
-taskname=
-
-#Simplify task change
-mapperfile=$tasknumb$taskname.py
-reducerfile="$tasknumb"reducer.py
-outfile=output$tasknumb
-
-#Automatic removal
-hadoop fs -rm -r $outfile
-
-#For Windows-compatibility
-apt-get install dos2unix
-dos2unix $mapperfile
-dos2unix $reducerfile
-
-#Main MapReduce function
-hadoop jar $HADOOP_HOME/share/hadoop/tools/lib/hadoop-streaming-2.7.3.jar \
--files $mapperfile,$reducerfile \
--mapper $mapperfile \
--reducer $reducerfile \
--input posts.xml \
--output $outfile
-
-#Read file and save it locally
-hadoop fs -cat $outfile/*
-hadoop fs -copyToLocal $outfile
-
-#Automatic cleanup
-hadoop fs -rm -r $outfile

### 2020-02-18 Article_Final/main.tex
Big D energy :)
My final edition of TexFile

@@
  \item Double: Assumes input "words" is comprised of two nested lists to print. Prints word, count in words as (word, count). Ignores empty strings and spaces.
- \item Triple: Assumes input "words" is comprised of three nested lists to print. Prints id, score, title in words as (id, score, title). does not ignore empty strings and spaces.
+ \item Triple: Assumes input "words" is comprised of three nested lists to print. Prints id, score, title in words as (id, score, title). Does not ignore empty strings and spaces.
 \end{itemize}
@@
 \subsection{\emph{Import sys}}
-The sys module is an open-source, built in python function that allows us to add to the module search path with sys.path.append(\'../\'), enabling finding ProjectFunctions in a parallel folder, and read in the input for our mapper function and reduce function using sys.stdin.
+The sys module is an open-source, built in python function that allows us to add to the module search path with sys.path.append('../../'), enabling finding ProjectFunctions in a parallel folder, and read in the input for our mapper function and reduce function using sys.stdin.
 \begin{lstlisting}[language=Python, caption=Import for sys]
 import sys
-sys.path.append(\'../\') #allows access functions in parallel folder
+sys.path.append('../../') #allows access functions in parallel folder
 import ProjectFunctions.functions as proj
@@
 \subsection{\emph{Data trimming}}
-We use the environment Docker, to act as a data cluster.
+We use the environment Docker as a virtual data cluster.
 Files that are bigger than 128MB are not readable by the module we use to parse XMLs within the Docker environment (whether this is due to this being the standard size of a data block we were not able to tell).
@@
 \textbf{Implementation}: This MapReduce job functions as 1a WordCount does, except it does not count the words and it looks through the titles instead of the bodies. \\ \\
-\textbf{Notes/Reflection}: Here again the choices made building the cleanBody function affects the output.
+\textbf{Notes/Reflection}: Here again the choices made building the cleanBody function affects the output, see "althalus".
 \lstinputlisting[firstline=500, lastline=510, title=1b\_output]{Code_output/output1b.txt}
@@
 \textbf{Implementation}: This mapper functions similarly to 1f tags, except instead of cleaning the tags, it uses "|" as a separator since spaces are part of the location.
-If Location is separated by a \',\' the last part is treated as the country.
+If Location is separated by a ',' the last part is treated as the country.
 \\ \\
-\textbf{Notes/Reflection}: Because by our judgment locations are typed in by users, we have elected to separate the country out of Location very simply by using \',\' as a separator.
-Anything after the last \',\' is treated as a country.
-A location with no \',\' is treated as a country.
+\textbf{Notes/Reflection}: Because by our judgement locations are typed in by users, we have elected to separate the country out of Location very simply by using ',' as a separator.
+Anything after the last ',' is treated as a country.
+A location with no ',' is treated as a country.
 Locations like "California, USA", "California, United States", and "US" will be interpreted as "usa", "united states", and "us", respectively.
-\lstinputlisting[firstline=1,lastline=10,title=2g\_output]{Code_output/output2g.txt}
+\lstinputlisting[firstline=101,lastline=110,title=2g\_output]{Code_output/output2g.txt}
 
@@
 \textbf{Notes/Reflection}: Here the most common name is User.
-This is due to our choice of removing numbers in cleanBody, combining User1, User2, User3, etc.
+This is likely due to our choice of removing numbers in cleanBody, combining User1, User2, User3, etc.
 The task suggested explicitly that we should split up names by spaces, perhaps wanting to separate out last names from first names.
@@
 \textbf{Notes/Reflection}: Having a combiner in a MapReduce job saves bandwidth and computational strain by decreasing the volume of data sent from the mapper, as shown in \ref{fig:figure_label}.
-\lstinputlisting[firstline=1,lastline=10,title=3c\_output]{Code_output/output3c.txt}
+\lstinputlisting[firstline=101,lastline=110,title=3c\_output]{Code_output/output3c.txt}
 

### 2020-02-23 Code/task2/task2c/run2c_windows.sh
xd

@@ -4,7 +4,7 @@
 
 #Simplify task change further
 taskNumber=2c
-taskName=TopMiners
+taskName=TopUsers
 sourceFile=Users
 
 #Simplify task change
